---
title: "Qualitative coding: category frequencies and inter-rater reliability"
author: "Anonymous"
date: "2026-09-17"
output: html_document
---

Reproduces the qualitative results reported in the paper's
"self-reported reasons for clicking" paragraph (Section 4.5), from
`Qualitative_coding.xlsx`:

* Cohen's kappa for the two independent coders, and the one disagreement on the
  clicking-reasons question;
* the seven open-text category frequencies plotted in the
  "Open-text (Other reasons)" panel of Figure 6 (`fig6_selfreportedreasons.pdf`).

Both are checked against the values printed in the paper, and the document stops
if either disagrees.

```{r setup}
suppressPackageStartupMessages({
  library(readxl)
  library(dplyr)
})

WORKBOOK <- "Qualitative_coding.xlsx"
options(width = 10000)  # tables print at full width, never wrapped

## run_analysis.sh writes everything this document prints to
## results/qualitative.log, laid out like analysis.log: section() opens each
## part with a numbered banner naming the part of the paper it supports, claim()
## marks the value a reported number is read from, and check() records each
## assertion as it passes. None of them touches the analysis.
section <- local({
  n <- 0
  function(title, paper, note = NULL) {
    n <<- n + 1
    rule <- strrep("#", 80)
    cat("\n\n", rule, "\n", sprintf("### %d. %s\n", n, title),
        sprintf("###    Paper: %s\n", paper), sep = "")
    if (!is.null(note)) cat(paste0("###    ", strwrap(note, 72), "\n"), sep = "")
    cat(rule, "\n\n", sep = "")
  }
})
## A claim longer than about 100 characters continues on indented lines, so
## '>>> ' still marks where each one starts.
claim <- function(...) {
  lines <- strwrap(paste0(...), width = 100, prefix = "    ", initial = ">>> ")
  lines <- gsub("([.?!])  ", "\\1 ", lines)  # strwrap doubles the space after a full stop
  cat("\n", paste0(lines, "\n"), sep = "")
}
check <- function(ok, what) {
  if (!isTRUE(ok)) stop("Does not match the paper: ", what, call. = FALSE)
  cat("Check passed: ", what, "\n", sep = "")
}
show <- function(df) print(as.data.frame(df), row.names = FALSE)
```

## The coding

Three free-text survey items were coded, each with its own codebook: the reasons
for clicking given after selecting "Other" (`reasons_click_6_TEXT`), what
participants did on the landing page (`read_content_2.2_3_TEXT`), and why they
read the follow-up content (`content_reasons`). Two raters coded every response
independently.

`Overview` carries all three side by side, plus `all_Rater 1` / `all_Rater 2`,
which stack the three codings into one pair of columns.

```{r read}
overview <- read_excel(WORKBOOK, sheet = "Overview")

## A rating is usable when both coders assigned a category. "x" is the coders'
## marker for a response they judged uncodable; blank means the row belongs to
## one of the other two questions.
usable <- function(df, c1, c2) {
  df |>
    transmute(rater1 = trimws(as.character(.data[[c1]])),
              rater2 = trimws(as.character(.data[[c2]]))) |>
    filter(!is.na(rater1), !is.na(rater2),
           rater1 != "", rater2 != "",
           tolower(rater1) != "x", tolower(rater2) != "x")
}
```

## Cohen's kappa

Unweighted, on the pooled coding of all three questions. This is the
$\kappa = 0.881$ the paper reports.

```{r kappa}
section("Inter-rater reliability, all three open-text questions pooled",
        "Section 4.5 (Self-reported reasons for clicking)",
        note = "Unweighted Cohen's kappa over every response both raters coded, across the three free-text items.")

cohens_kappa <- function(ratings) {
  categories <- sort(unique(c(ratings$rater1, ratings$rater2)))
  tab <- table(factor(ratings$rater1, levels = categories),
               factor(ratings$rater2, levels = categories))
  n  <- sum(tab)
  po <- sum(diag(tab)) / n
  pe <- sum(rowSums(tab) * colSums(tab)) / n^2
  list(n = n, po = po, kappa = (po - pe) / (1 - pe))
}

pooled <- usable(overview, "all_Rater 1", "all_Rater 2")
k <- cohens_kappa(pooled)

cat(sprintf("Responses coded by both raters  %d\n", k$n))
cat(sprintf("Observed agreement              %.3f\n", k$po))
claim("Section 4.5: Cohen's kappa = 0.881")
cat(sprintf("Cohen's kappa                   %.3f\n\n", k$kappa))

check(k$n == 120 && round(k$kappa, 3) == 0.881,
      "pooled kappa = 0.881 over 120 coded responses")
```

Per question, for context. The paper quotes only the pooled kappa; of the
per-question figures it uses only the clicking-reasons question's single
disagreement.

```{r kappa-per-question}
section("Inter-rater reliability per question",
        "Section 4.5 (one disagreement in 34 clicking-reasons responses)",
        note = "The per-question kappas are not reported in the paper.")

per_question <- list(
  "reasons_click_6_TEXT"    = c("6labels_Rater 1", "6labels_Rater 2"),
  "read_content_2.2_3_TEXT" = c("3labels_Rater 1", "3labels_Rater 2"),
  "content_reasons"         = c("clabels_Rater 1", "clabels_Rater 2")
)

per_q <- bind_rows(lapply(names(per_question), function(q) {
  r  <- usable(overview, per_question[[q]][1], per_question[[q]][2])
  kq <- cohens_kappa(r)
  data.frame(question = q, coded = kq$n, disagreements = sum(r$rater1 != r$rater2),
             agreement = round(kq$po, 3), kappa = round(kq$kappa, 3))
}))

claim("Section 4.5: the raters disagreed on one of 34 clicking-reasons responses: the reasons_click_6_TEXT row")
show(per_q)
cat("\n")

check(per_q$coded[1] == 34 && per_q$disagreements[1] == 1,
      "one disagreement among 34 clicking-reasons responses")
```

## Open-text category frequencies

The codebook, including each category's number, is on the `Categories` sheet.

The frequencies the paper plots are the second coder's column. The two coders
differ on exactly one of these 34 responses (rater 1 codes it "Legitimate
Appearance", rater 2 "Situational Fit"), and the published counts follow rater
2, as the paper states.

```{r frequencies}
section("Open-text reasons for clicking: category counts; Figure 6",
        "Section 4.5; Figure 6 (fig:selfreportedreasons), the 'Open-text (Other reasons)' panel",
        note = "Counts of the second rater's codes on reasons_click_6_TEXT, beside the frequencies recorded in the coders' codebook. 'in Figure 6' is the bar's label in the paper; the two pairs of categories with equal counts are matched to their bars by name.")

codebook <- read_excel(WORKBOOK, sheet = "Categories") |>
  filter(!is.na(`category name`)) |>
  transmute(question = question,
            code     = as.character(`coded as`),
            category = `category name`,
            recorded = as.integer(frequency))

## `question` is filled in only on the first row of each block.
codebook$question <- Reduce(function(a, b) if (is.na(b)) a else b,
                            codebook$question, accumulate = TRUE)

clicking <- codebook |> filter(question == "reasons_click_6_TEXT")

ratings <- usable(overview, "6labels_Rater 1", "6labels_Rater 2")

cat("The one disagreement, by category:\n")
ratings |>
  filter(rater1 != rater2) |>
  mutate(rater1 = clicking$category[match(rater1, clicking$code)],
         rater2 = clicking$category[match(rater2, clicking$code)]) |>
  rename(`rater 1` = rater1, `rater 2 (adopted)` = rater2) |>
  show()
cat("\n")

in_figure <- c(
  "Situational Fit"          = "Situational fit",
  "Distraction"              = "Distracted / stressed / multitasking",
  "Mobile Use"               = "On mobile device",
  "Legitimate Appearance"    = "Seemed legitimate / curiosity",
  "Awareness"                = "Did not expect phishing",
  "External Email Security"  = "Did not know how to differentiate",
  "External Email Labelling" = "Not marked as external"
)

result <- clicking |>
  select(code, category, recorded) |>
  left_join(count(ratings, code = rater2, name = "derived"), by = "code") |>
  mutate(derived = ifelse(is.na(derived), 0L, derived),
         `in Figure 6` = unname(in_figure[category])) |>
  arrange(desc(derived))

claim("Section 4.5, Figure 6: open-text counts 13 / 12 / 3 / 2 / 2 / 1 / 1: the derived column")
show(result)
cat(sprintf("\nTotal coded responses           %d\n\n", sum(result$derived)))

check(identical(result$derived, result$recorded),
      "every derived count equals the codebook's recorded frequency")
check(identical(as.integer(result$derived), c(13L, 12L, 3L, 2L, 2L, 1L, 1L)),
      "the counts are the paper's 13 / 12 / 3 / 2 / 2 / 1 / 1")
```

These are the seven bars of the paper's "Open-text (Other reasons)" panel:
situational fit 13, distraction 12, mobile use 3, legitimate appearance 2,
awareness 2, external email security 1, external email labelling 1.

## The closed-format counts live in the other document

The four **closed-format** counts in the same figure (thought the email was
legitimate, 40; security system would protect me, 6; clicked to check whether it
was phishing, 4; did not read the content, 3) come from the multi-select
`reasons_click` item in the survey data, not from this coding workbook, so
`Repeat_clicker_analysis_5.Rmd` derives and asserts them instead. They need no
filter beyond the analysis sample itself: 67 of the 986 answered the item.
