---
title: "Qualitative coding: category frequencies and inter-rater reliability"
author: "Anonymous"
date: "2026-09-17"
output: html_document
---

Reproduces the two qualitative results reported in the paper's
"self-reported reasons for clicking" paragraph, from `Qualitative_coding.xlsx`:

* Cohen's kappa for the two independent coders;
* the seven open-text category frequencies plotted in the
  "Open-text (Other reasons)" panel of
  `self_reported_reasons_clicking_faceted.pdf`.

Both are checked against the values printed in the paper, and the document stops
if either disagrees.

```{r setup}
library(readxl)
library(dplyr)

WORKBOOK <- "Qualitative_coding.xlsx"
```

## The coding

Three free-text survey items were coded, each with its own codebook: the reasons
for clicking given after selecting "Other" (`reasons_click_6_TEXT`), what
participants did on the landing page (`read_content_2.2_3_TEXT`), and why they
read the follow-up content (`content_reasons`). Two raters coded every response
independently.

`Overview` carries all three side by side, plus `all_Rater 1` / `all_Rater 2`,
which stack the three codings into one pair of columns.

```{r read}
overview <- read_excel(WORKBOOK, sheet = "Overview")

## A rating is usable when both coders assigned a category. "x" is the coders'
## marker for a response they judged uncodable; blank means the row belongs to
## one of the other two questions.
usable <- function(df, c1, c2) {
  df |>
    transmute(rater1 = trimws(as.character(.data[[c1]])),
              rater2 = trimws(as.character(.data[[c2]]))) |>
    filter(!is.na(rater1), !is.na(rater2),
           rater1 != "", rater2 != "",
           tolower(rater1) != "x", tolower(rater2) != "x")
}
```

## Cohen's kappa

Unweighted, on the pooled coding of all three questions. This is the
$\kappa = 0.881$ the paper reports.

```{r kappa}
cohens_kappa <- function(ratings) {
  categories <- sort(unique(c(ratings$rater1, ratings$rater2)))
  tab <- table(factor(ratings$rater1, levels = categories),
               factor(ratings$rater2, levels = categories))
  n  <- sum(tab)
  po <- sum(diag(tab)) / n
  pe <- sum(rowSums(tab) * colSums(tab)) / n^2
  list(n = n, po = po, kappa = (po - pe) / (1 - pe))
}

pooled <- usable(overview, "all_Rater 1", "all_Rater 2")
k <- cohens_kappa(pooled)

cat("N ratings           =", k$n, "\n")
cat("Observed agreement  =", round(k$po, 3), "\n")
cat("Cohen's kappa       =", round(k$kappa, 3), "\n")

stopifnot(k$n == 120, round(k$kappa, 3) == 0.881)
```

Per question, for context. The paper quotes only the pooled value, so the
per-question figures below are not in the manuscript.

```{r kappa-per-question}
per_question <- list(
  "reasons_click_6_TEXT"    = c("6labels_Rater 1", "6labels_Rater 2"),
  "read_content_2.2_3_TEXT" = c("3labels_Rater 1", "3labels_Rater 2"),
  "content_reasons"         = c("clabels_Rater 1", "clabels_Rater 2")
)

for (q in names(per_question)) {
  cols <- per_question[[q]]
  kq <- cohens_kappa(usable(overview, cols[1], cols[2]))
  cat(sprintf("%-26s N = %3d  agreement = %.3f  kappa = %.3f\n",
              q, kq$n, kq$po, kq$kappa))
}
```

## Open-text category frequencies

The codebook, including each category's number, is on the `Categories` sheet.

```{r codebook}
codebook <- read_excel(WORKBOOK, sheet = "Categories") |>
  filter(!is.na(`category name`)) |>
  transmute(question = question,
            code     = as.character(`coded as`),
            category = `category name`,
            recorded = as.integer(frequency))

## `question` is filled in only on the first row of each block.
codebook$question <- Reduce(function(a, b) if (is.na(b)) a else b,
                            codebook$question, accumulate = TRUE)

clicking <- codebook |> filter(question == "reasons_click_6_TEXT")
print(clicking)
```

The frequencies the paper plots are the second coder's column. The two coders
differ on exactly one of these 34 responses (rater 1 codes it "Legitimate
Appearance", rater 2 "Situational Fit"), and the published counts follow rater
2, which is consistent with the paper's statement that disagreements were
resolved by discussion.

```{r frequencies}
counts <- usable(overview, "6labels_Rater 1", "6labels_Rater 2") |>
  count(code = rater2, name = "derived")

result <- clicking |>
  select(code, category, recorded) |>
  left_join(counts, by = "code") |>
  mutate(derived = ifelse(is.na(derived), 0L, derived)) |>
  arrange(desc(derived))

print(result)
cat("Total coded responses =", sum(result$derived), "\n")

stopifnot(identical(result$derived, result$recorded))
```

These are the seven bars of the paper's "Open-text (Other reasons)" panel:
situational fit 13, distraction 12, mobile use 3, legitimate appearance 2,
awareness 2, external email security 1, external email labelling 1.

## The closed-format counts live in the other document

The four **closed-format** counts in the same figure (thought the e-mail was
legitimate, 40; security system would protect me, 6; clicked to check whether it
was phishing, 4; did not read the content, 3) come from the multi-select
`reasons_click` item in the survey data, not from this coding workbook, so
`Repeat_clicker_analysis_5.Rmd` derives and asserts them instead. They need no
filter beyond the analysis sample itself: 67 of the 986 answered the item.
