---
title: "Anonymous"
author: "Anonymous"
date: "2025-06-17"
output: html_document
---

 
```{r}

 
## -------------------------------------------------
## 0) Setup
## -------------------------------------------------
set.seed(123)


knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)

packages <- c(
  "readxl", "dplyr", "readr", "lavaan", "semTools", "lubridate",
  "stringr", "tidyr", "Hmisc", "ggplot2", "moments", "patchwork",
  "mice", "lmtest", "car", "tools", "lme4", "miceadds", "DescTools"
)

installed <- packages %in% rownames(installed.packages())
if (any(!installed)) install.packages(packages[!installed])
lapply(packages, library, character.only = TRUE)


## -------------------------------------------------
## 1) Read raw data
## -------------------------------------------------

df_raw <- read_excel("study_data_merged.xlsx")


num_cols <- c(
  "Optimism_bias_self_1", "Optimism_bias_self_2",
  "Optimism_bias_other_1", "Optimism_bias_other_2",
  paste0("self_efficacy_", 1:4),
  paste0("risk_perception_", 1:6),
  paste0("locus_of_control_", 1:12),
  paste0("Acceptance _", 1:8),
  paste0("negative_emotions_", 1:13),
  paste0("Training intention _", 1:5),
  paste0("Q21_", 1:3),
  paste0("Q22_", 1:2)
)


cat("Raw duplicates (by anonymisedEmail): ",
    sum(duplicated(df_raw$anonymisedEmail)), "\n")




## -------------------------------------------------
## 2) Parse numerics + reverse code
## -------------------------------------------------

rev_items <- paste0("locus_of_control_", c(1,2,6,7,8,9,10,11))

df_clean <- df_raw %>%
  mutate(
    across(all_of(num_cols), ~ parse_number(as.character(.))),
    across(all_of(rev_items), ~ 8 - .),

    # Years at the organisation, collected in ordered five-year groups. The
    # dataset carries the band labels directly; the stopifnot below asserts
    # that every label is one of the expected bands.
    years_org_group = trimws(as.character(`[anonymized institution]_years_groups`)),
    years_org = factor(
      years_org_group,
      levels = c("1-5", "6-10", "11-15", "16-20", "21-25", "26-30", "31+"),
      ordered = TRUE
    ),
    years_org_num = as.numeric(years_org)
  )

## Guard: an unrecognised tenure band must never pass silently as NA. If this
## fires, the band labels in the input are not the expected "1-5" ... "31+".
stopifnot(!any(is.na(df_clean$years_org) &
                 !is.na(df_clean$`[anonymized institution]_years_groups`)))


## -------------------------------------------------
## 3) Check: t-Test for duplicated values --> different? 
##    Remove duplicates
##    Rule: take first occurrence per anonymisedEmail
## -------------------------------------------------
dup_emails <- df_clean %>%
  count(anonymisedEmail) %>%
  filter(n > 1) %>%
  pull(anonymisedEmail)

if (length(dup_emails) > 0) {
  
  df_dup <- df_clean %>%
    filter(anonymisedEmail %in% dup_emails) %>%
    mutate(
      optimism_bias =
        rowMeans(across(c(Optimism_bias_other_1, Optimism_bias_other_2)),
                 na.rm = TRUE) -
        rowMeans(across(c(Optimism_bias_self_1,  Optimism_bias_self_2)),
                 na.rm = TRUE),
      self_efficacy      = rowMeans(across(self_efficacy_1:self_efficacy_4), na.rm = TRUE),
      risk_perception    = rowMeans(across(c(risk_perception_1:risk_perception_4,
                                             risk_perception_6)),
                                    na.rm = TRUE),
      locus_of_control   = rowMeans(across(locus_of_control_1:locus_of_control_12),
                                    na.rm = TRUE),
      acceptance         = rowMeans(across(c(`Acceptance _1`:`Acceptance _6`,
                                             `Acceptance _8`)),
                                    na.rm = TRUE),
      negative_emotions  = rowMeans(across(c(negative_emotions_1:negative_emotions_10,
                                             negative_emotions_12:negative_emotions_13)),
                                    na.rm = TRUE),
      training_intention = rowMeans(across(`Training intention _1`:`Training intention _5`),
                                    na.rm = TRUE)
    ) %>%
    group_by(anonymisedEmail) %>%
    mutate(entry = row_number()) %>%
    ungroup()
  
  df_wide <- df_dup %>%
    dplyr::select(anonymisedEmail, entry,
           optimism_bias, self_efficacy, risk_perception,
           locus_of_control, acceptance, negative_emotions,
           training_intention) %>%
    pivot_wider(
      names_from  = entry,
      values_from = c(optimism_bias, self_efficacy, risk_perception,
                      locus_of_control, acceptance, negative_emotions,
                      training_intention),
      names_sep = "_entry"
    )
  
  test_vars <- c("optimism_bias", "self_efficacy", "risk_perception",
                 "locus_of_control", "acceptance", "negative_emotions",
                 "training_intention")
  
  paired_results <- lapply(test_vars, function(var) {
    v1 <- paste0(var, "_entry1")
    v2 <- paste0(var, "_entry2")
    t_res <- t.test(df_wide[[v1]], df_wide[[v2]], paired = TRUE)
    data.frame(
      variable  = var,
      t_stat    = unname(t_res$statistic),
      df        = unname(t_res$parameter),
      p_value   = unname(t_res$p.value),
      mean_diff = mean(df_wide[[v1]] - df_wide[[v2]], na.rm = TRUE)
    )
  })
  
  paired_results_df <- bind_rows(paired_results)
  cat("\nPaired t-tests duplicate entries (pre-dedupe):\n")
  print(paired_results_df)
}


## -------------------------------------------------
## 4) Remove duplicates (exluding the second value)
## -------------------------------------------------
df_dedup <- df_clean %>%
  group_by(anonymisedEmail) %>%
  slice(1) %>%
  ungroup()

cat("Unique participants after dedupe: ", nrow(df_dedup), "\n")


## -------------------------------------------------
## 5) Attention checks
##    We'll compute all variants once.
## -------------------------------------------------

# Helper: number of passed checks per row
df_checks <- df_dedup %>%
  mutate(
    pass1 = risk_perception_5    == 1,
    pass2 = `Acceptance _7`      == 3,
    pass3 = negative_emotions_11 == 1,
    n_pass = rowSums(cbind(pass1, pass2, pass3), na.rm = TRUE)
  )

n_total <- nrow(df_checks)

### 4a) strict = all 3 correct
df_strict <- df_checks %>%
  filter(
    risk_perception_5    == 1,
    `Acceptance _7`      == 3,
    negative_emotions_11 == 1
  ) %>%
  dplyr::select(-pass1, -pass2, -pass3, -n_pass)

cat("\n[Strict check]\n")
cat(" Kept:        ", nrow(df_strict), "\n")
cat(" Excluded:    ", n_total - nrow(df_strict), "\n")
cat(" Excluded %:  ",
    round(100 * (n_total - nrow(df_strict)) / n_total, 1), "%\n", sep="")

### 4b) max 2 fails = at least 1 correct  (n_pass >= 1)
df_max2fail <- df_checks %>%
  filter(n_pass >= 1) %>%
  dplyr::select(-pass1, -pass2, -pass3, -n_pass)

cat("\n[Max 2 fails]\n")
cat(" Kept (>=1 ok): ", nrow(df_max2fail), "\n")
cat(" Excluded:      ", n_total - nrow(df_max2fail), "\n")

### 4c) min 2 correct = n_pass >= 2
df_min2pass <- df_checks %>%
  filter(n_pass >= 2) %>%
  dplyr::select(-pass1, -pass2, -pass3, -n_pass)

cat("\n[Min 2 correct]\n")
cat(" Kept (>=2 ok): ", nrow(df_min2pass), "\n")
cat(" Excluded:      ", n_total - nrow(df_min2pass), "\n\n")


## -------------------------------------------------
## Decision for dataset to continue with:
## -------------------------------------------------

df_analysis <- df_strict


##-------------------------------------------------
##Exclusion of those participants who a. did not read or deleted the email
##-------------------------------------------------



to_valid <- function(x) {
  x <- trimws(as.character(x))
  ifelse(is.na(x) | x == "" | x == "--", 0L, 1L)
}

df_analysis_filt <- df_analysis %>%
  mutate(
    read_sim1    = to_valid(sim1_MessageRead_TimeStamp),
    read_sim2    = to_valid(sim2_MessageRead_TimeStamp),
    del_sim1     = to_valid(sim1_MessageDeleted_TimeStamp),
    del_sim2     = to_valid(sim2_MessageDeleted_TimeStamp),
    processed_sim1 = ifelse(read_sim1 == 1L | del_sim1 == 1L, 1L, 0L),
    processed_sim2 = ifelse(read_sim2 == 1L | del_sim2 == 1L, 1L, 0L)
  ) %>%
  filter(processed_sim1 == 1L, processed_sim2 == 1L)



cat("N vorher:", nrow(df_analysis), "\n")
cat("N nach Read-Filter:", nrow(df_analysis_filt), "\n")





##-------------------------------------------------
## 6) Straightlining
##-------------------------------------------------

 
items_all <- c(
  "Optimism_bias_self_1","Optimism_bias_self_2",
  "Optimism_bias_other_1","Optimism_bias_other_2",
  paste0("self_efficacy_", 1:4),
  paste0("risk_perception_", 1:6),
  paste0("locus_of_control_", 1:12),          
  paste0("Acceptance _", 1:8),
  paste0("negative_emotions_", 1:13),
  paste0("Training intention _", 1:5),
  paste0("Q21_", 1:3), paste0("Q22_", 1:2)
)

 
.longstring_vec <- function(x) {
  if (all(is.na(x))) return(NA_integer_)
  s <- split(x, cumsum(is.na(x)))                      
  runs <- unlist(lapply(s, function(v) if (length(v)) rle(v)$lengths else integer()))
  if (length(runs)) max(runs) else 0L
}
.n_runs_ge_x <- function(x, X = 12) {
  if (all(is.na(x))) return(NA_integer_)
  s <- split(x, cumsum(is.na(x)))
  runs <- unlist(lapply(s, function(v) if (length(v)) rle(v)$lengths else integer()))
  sum(runs >= X)
}
.prop_same_adj <- function(x) {
  v <- x[!is.na(x)]
  if (length(v) < 2) return(NA_real_)
  mean(v[-1] == v[-length(v)])
}
.irv <- function(x) {
  v <- x[!is.na(x)]
  if (length(v) < 2) return(NA_real_)
  stats::sd(v)
}

 
 
scale01 <- function(v) {
  if (all(is.na(v))) return(v)
  vnum <- as.numeric(v)
  vmin <- 1
  vmax <- max(vnum, na.rm = TRUE)
  out <- (vnum - vmin) / (vmax - vmin)
  round(out, 2)                                     
}

df_seq <- df_analysis_filt %>%
  dplyr::select(anonymisedEmail, all_of(items_all)) %>%
  mutate(across(all_of(items_all), scale01))


 
threshold_X <- 12

straight_all <- df_seq |>
  dplyr::rowwise() |>
  dplyr::mutate(
    longstring_all    = .longstring_vec(dplyr::c_across(dplyr::all_of(items_all))),
    n_runs_ge_12_all  = .n_runs_ge_x(dplyr::c_across(dplyr::all_of(items_all)), X = threshold_X),
    prop_same_adj_all = .prop_same_adj(dplyr::c_across(dplyr::all_of(items_all))),
    irv_all           = .irv(dplyr::c_across(dplyr::all_of(items_all))),
    flag_ge_12_all    = longstring_all >= threshold_X
  ) |>
  dplyr::ungroup() |>
  dplyr::select(anonymisedEmail, longstring_all, n_runs_ge_12_all,
                prop_same_adj_all, irv_all, flag_ge_12_all)

 
straight_all |>
  dplyr::arrange(dplyr::desc(longstring_all)) |>
  print(n = 20)

 
if (!requireNamespace("ggplot2", quietly = TRUE)) install.packages("ggplot2")


 
ggplot(straight_all, aes(x = longstring_all)) +
  geom_histogram(binwidth = 1, color = "black", fill = "steelblue") +
  geom_text(
    stat = "count",
    aes(label = ..count..),
    vjust = -0.3,
    size = 3.5
  ) +
  labs(
    title = "Distribution of LongString-Werte across all items",
    x = "Longest series with same answer",
    y = "Frequency (Number of persons"
  ) +
  theme_minimal(base_size = 13)

 
straight_all %>%
  filter(longstring_all >= 12) %>%
  dplyr::select(anonymisedEmail, longstring_all, irv_all) %>%
  arrange(desc(longstring_all))

## -------------------------------------------------
## Alternative dataset without extreme straightliners (cutoff ≥ 18)
## -------------------------------------------------


straightliner_ids <- straight_all %>%
  filter(longstring_all >= 18) %>%
  pull(anonymisedEmail)

cat("\nAnzahl Straightliner (>=18 gleiche Antworten in Folge): ",
    length(straightliner_ids), "\n")


df_analysis_filt_noSL <- df_analysis_filt %>%
  filter(!anonymisedEmail %in% straightliner_ids)

cat("N Original (df_analysis_filt): ", nrow(df_analysis_filt), "\n")
cat("N ohne Straightliner    : ", nrow(df_analysis_filt_noSL), "\n")




## -------------------------------------------------
## 7) Create composite scores on analysis sample
## -------------------------------------------------

df_analysis_filt <- df_analysis_filt %>%
  mutate(
    optimism_bias =
      rowMeans(across(c(Optimism_bias_other_1, Optimism_bias_other_2)),
               na.rm = TRUE) -
      rowMeans(across(c(Optimism_bias_self_1,  Optimism_bias_self_2)),
               na.rm = TRUE),

    self_efficacy      = rowMeans(across(self_efficacy_1:self_efficacy_4), na.rm = TRUE),
    risk_perception    = rowMeans(across(c(risk_perception_1:risk_perception_4,
                                           risk_perception_6)),
                                  na.rm = TRUE),
    locus_of_control   = rowMeans(across(locus_of_control_1:locus_of_control_12),
                                  na.rm = TRUE),
    acceptance         = rowMeans(across(c(`Acceptance _1`:`Acceptance _6`,
                                           `Acceptance _8`)),
                                  na.rm = TRUE),
    negative_emotions  = rowMeans(across(c(negative_emotions_1:negative_emotions_10,
                                           negative_emotions_12:negative_emotions_13)),
                                  na.rm = TRUE),
    training_intention = rowMeans(across(`Training intention _1`:`Training intention _5`),
                                  na.rm = TRUE),
    per_orga_security  = rowMeans(across(Q21_1:Q21_3), na.rm = TRUE),
    feeling_attacked   = rowMeans(across(Q22_1:Q22_2), na.rm = TRUE)
  )

unique(df_analysis_filt$JobRole_std)


## -------------------------------------------------
## 8) Simulation behaviour indicators
##    clicked / compromised / reported across all sims
## -------------------------------------------------

to_indicator <- function(x) {
  x <- trimws(as.character(x))
  dplyr::case_when(
    is.na(x) | x == "" ~ NA_integer_,
    x == "--"          ~ 0L,
    TRUE               ~ 1L
  )
}

df_analysis_filt <- df_analysis_filt %>%
  mutate(
    # clicked
    clicked_sim0  = to_indicator(`sim0_Viewed Landing Page_Time_c1_2023-03-29`),
    clicked_sim05 = to_indicator(`sim0.5_Viewed Landing Page_Time_c2_2024-07-22`),
    clicked_sim1  = to_indicator(sim1_EmailLinkClicked_TimeStamp),
    clicked_sim2  = to_indicator(sim2_EmailLinkClicked_TimeStamp),
    clicked       = clicked_sim0 + clicked_sim05 + clicked_sim1 + clicked_sim2,

    # compromised
    compromised_sim0  = to_indicator(`sim0_Data Entered_Time_c1_2023-03-29`),
    compromised_sim05 = to_indicator(`sim0.5_Data Entered_Time_c2_2024-07-22`),
    compromised_sim1  = to_indicator(sim1_CredSupplied_TimeStamp_Compromised),
    compromised_sim2  = to_indicator(sim2_CredSupplied_TimeStamp_Compromised),
    compromised       = compromised_sim0 + compromised_sim05 +
                        compromised_sim1 + compromised_sim2,

    # reported
    reported_sim1 = to_indicator(sim1_Phishing_Reported_On),
    reported_sim2 = to_indicator(sim2_Phishing_Reported_On),
    reported      = reported_sim1 + reported_sim2
  )


lapply(
  c("clicked_sim0","clicked_sim05","clicked_sim1","clicked_sim2",
    "compromised_sim0","compromised_sim05","compromised_sim1","compromised_sim2",
    "reported_sim1","reported_sim2"),
  \(v) { cat("\n", v, "\n"); print(table(df_analysis_filt[[v]], useNA="ifany")) }
)





## -------------------------------------------------
## 9) Missingness check for key predictors
## -------------------------------------------------

key_preds <- c("optimism_bias", "risk_perception", "negative_emotions",
               "acceptance", "self_efficacy", "locus_of_control")

n_complete <- sum( complete.cases(df_analysis_filt[ key_preds ]) )
cat("\nComplete cases for predictors: ", n_complete, "\n")

df_analysis_filt %>% summarise(n_missing_locus = sum(is.na(locus_of_control))) %>% print()
df_analysis_filt %>% summarise(n_missing_opt   = sum(is.na(optimism_bias)))  %>% print()
df_analysis_filt %>% summarise(n_missing_rp1   = sum(is.na(risk_perception_1))) %>% print()
df_analysis_filt %>% summarise(n_missing_se    = sum(is.na(self_efficacy)))  %>% print()
df_analysis_filt %>% summarise(n_missing_ne    = sum(is.na(negative_emotions))) %>% print()
df_analysis_filt %>% summarise(n_missing_acc   = sum(is.na(acceptance))) %>% print()


## -------------------------------------------------
## 10) Correlations between composites + behaviour
## -------------------------------------------------

corr_vars <- df_analysis_filt %>%
  dplyr::select(
    optimism_bias, self_efficacy, risk_perception, locus_of_control,
    acceptance, negative_emotions, training_intention,
    per_orga_security, feeling_attacked
  )

corr_matrix <- cor(corr_vars, use = "pairwise.complete.obs")


res <- rcorr(as.matrix(corr_vars), type = "pearson")
Rmat <- res$r
Pmat <- res$P

stars <- symnum(
  Pmat, corr = FALSE, na = FALSE,
  cutpoints = c(0, 0.001, 0.01, 0.05, 1),
  symbols   = c("***", "**", "*", " ")
)

Rstars <- matrix(
  paste0(formatC(Rmat, format = "f", digits = 2), stars),
  ncol = ncol(Rmat),
  dimnames = dimnames(Rmat)
)

cat("\nCorrelation matrix with sig stars:\n")
print(Rstars)


## -------------------------------------------------
## 11) Descriptives for phishing outcomes
## -------------------------------------------------

cat("\nClicked summary:\n")
df_analysis_filt %>%
  count(clicked) %>%
  mutate(pct = round(100 * n / sum(n), 1)) %>%
  print()

cat("\nCompromised summary:\n")
df_analysis_filt %>%
  count(compromised) %>%
  mutate(pct = round(100 * n / sum(n), 1)) %>%
  print()

cat("\nReported summary:\n")
df_analysis_filt %>%
  count(reported) %>%
  mutate(pct = round(100 * n / sum(n), 1)) %>%
  print()


##--------------------------------------------------
## 12) Summary per simulation (percentages)
##--------------------------------------------------

sim_summary <- tibble(
  sim = c("sim0", "sim0.5", "sim1", "sim2"),
  clicked_rate = c(
    mean(df_analysis_filt$clicked_sim0,  na.rm = TRUE),
    mean(df_analysis_filt$clicked_sim05, na.rm = TRUE),
    mean(df_analysis_filt$clicked_sim1,  na.rm = TRUE),
    mean(df_analysis_filt$clicked_sim2,  na.rm = TRUE)
  ) * 100,
  compromised_rate = c(
    mean(df_analysis_filt$compromised_sim0,  na.rm = TRUE),
    mean(df_analysis_filt$compromised_sim05, na.rm = TRUE),
    mean(df_analysis_filt$compromised_sim1,  na.rm = TRUE),
    mean(df_analysis_filt$compromised_sim2,  na.rm = TRUE)
  ) * 100,
  reported_rate = c(
    NA,  # sim0 hatte kein Reporting
    NA,  # sim0.5 auch nicht
    mean(df_analysis_filt$reported_sim1, na.rm = TRUE) * 100,
    mean(df_analysis_filt$reported_sim2, na.rm = TRUE) * 100
  )
)
print(sim_summary)


##----------------------------------
## 13) Age and Job role stats
##----------------------------------


names(df_analysis_filt)

## Midpoints of the age bands; the top band is labelled "65+". A level that
## matched nothing would come back from dplyr::recode as NA and be silently
## dropped by mean(..., na.rm = TRUE), and warnings are suppressed by the chunk
## options, so the guard below checks for it explicitly.
df_analysis_filt$age_mean <- dplyr::recode(df_analysis_filt$Age,
  "18-24" = 21,
  "25-34" = 29.5,
  "35-44" = 39.5,
  "45-54" = 49.5,
  "55-64" = 59.5,
  "65+"   = 69.5   # open-ended band; 69.5 assumes an effective 65-74 span
)

## Guard: an unmatched level must never pass silently.
stopifnot(!any(is.na(df_analysis_filt$age_mean) & !is.na(df_analysis_filt$Age)))


mean(df_analysis_filt$age_mean, na.rm = TRUE)

sd(df_analysis_filt$age_mean, na.rm = TRUE)

df_analysis_filt <- df_analysis_filt %>%
  mutate(
    JobRole_bin = factor(
      ifelse(JobRole_std == "academic",
             "academic",
             "non-academic"),
      levels = c("academic", "non-academic")
    )
  )




table(df_analysis_filt$JobRole_bin)

levels(df_analysis_filt$JobRole_bin)


prop.table(table(df_analysis_filt$JobRole_std))


##-----------------------------------
## 14) Reporting
##-----------------------------------
df_analysis_filt <- df_analysis_filt %>%
  mutate(
    reporting_sim1  = to_indicator(sim1_Phishing_Reported_On),
    reporting_sim2  = to_indicator(sim2_Phishing_Reported_On),

    reporting_total = 
                      reporting_sim1 + reporting_sim2
  )
df_analysis_filt %>%
  summarise(
    sim1  = mean(reporting_sim1  == 1, na.rm = TRUE) * 100,
    sim2  = mean(reporting_sim2  == 1, na.rm = TRUE) * 100
  )

##-----------------------------------
## 15) difficulty rating
## -------------------------------------------------

difficulty_consensus <- tibble(
  email_id = c(1, 2, 3, 4),
  difficulty_ord = c(1, 2, 2, 3)
)

df_analysis_filt <- df_analysis_filt %>%
  mutate(
    difficulty_email1 = difficulty_consensus$difficulty_ord[ difficulty_consensus$email_id == 1 ],
    difficulty_email2 = difficulty_consensus$difficulty_ord[ difficulty_consensus$email_id == 2 ],
    difficulty_email3 = difficulty_consensus$difficulty_ord[ difficulty_consensus$email_id == 3 ],
    difficulty_email4 = difficulty_consensus$difficulty_ord[ difficulty_consensus$email_id == 4 ]
    

  )



##------------------------
##Reporting
##------------------------

is_reported_val <- function(x) {
  x <- trimws(as.character(x))
  !is.na(x) & x != "" & x != "--"
}


df_analysis_filt$reported_sim1 <- is_reported_val(df_analysis_filt$sim1_Phishing_Reported_On)
df_analysis_filt$reported_sim2 <- is_reported_val(df_analysis_filt$sim2_Phishing_Reported_On)


df_analysis_filt$reported_any <- df_analysis_filt$reported_sim1 | df_analysis_filt$reported_sim2

df_analysis_filt$reported_when <- ifelse(df_analysis_filt$reported_sim1 & df_analysis_filt$reported_sim2, "both",
                            ifelse(df_analysis_filt$reported_sim1, "sim1",
                            ifelse(df_analysis_filt$reported_sim2, "sim2", "none")))
df_analysis_filt$reported_when <- factor(
  df_analysis_filt$reported_when,
  levels = c("none", "sim1", "sim2", "both")
)


total_sample <- nrow(df_analysis_filt)


counts <- c(
  total = total_sample,
  sim1  = sum(df_analysis_filt$reported_sim1),
  sim2  = sum(df_analysis_filt$reported_sim2),
  any   = sum(df_analysis_filt$reported_any),
  both  = sum(df_analysis_filt$reported_sim1 & df_analysis_filt$reported_sim2)
)

rates <- counts / total_sample

counts
rates




##------------------------
##Cronbach's alpha
##------------------------

alphas <- list(

  optimism_self = psych::alpha(
    df_analysis_filt %>% select(Optimism_bias_self_1, Optimism_bias_self_2)
  ),

  optimism_other = psych::alpha(
    df_analysis_filt %>% select(Optimism_bias_other_1, Optimism_bias_other_2)
  ),

  self_efficacy = psych::alpha(
    df_analysis_filt %>% select(self_efficacy_1:self_efficacy_4)
  ),

  risk_perception = psych::alpha(
    df_analysis_filt %>% 
      select(risk_perception_1:risk_perception_4,
             risk_perception_6)
  ),

  locus_of_control = psych::alpha(
    df_analysis_filt %>% select(locus_of_control_1:locus_of_control_12)
  ),

  acceptance = psych::alpha(
    df_analysis_filt %>%
      select(`Acceptance _1`:`Acceptance _6`,
             `Acceptance _8`)
  ),

  negative_emotions = psych::alpha(
    df_analysis_filt %>%
      select(negative_emotions_1:negative_emotions_10,
             negative_emotions_12:negative_emotions_13)
  ),

  training_intention = psych::alpha(
    df_analysis_filt %>% select(`Training intention _1`:`Training intention _5`)
  ),

  per_orga_security = psych::alpha(
    df_analysis_filt %>% select(Q21_1:Q21_3)
  ),

  feeling_attacked = psych::alpha(
    df_analysis_filt %>% select(Q22_1:Q22_2)
  )
)



lapply(names(alphas), function(n) {
  cat(sprintf("%-22s α = %.3f\n", n, alphas[[n]]$total$raw_alpha))
})
```


#Assumption checks:
```{r}
 ## -------------------------------------------------
## Assumption checks (uses df_analysis_filt)
## -------------------------------------------------

## 1) Distribution diagnostics --------------------------------

vars_to_check <- c(
  
  "clicked_sim0", "clicked_sim05", "clicked_sim1", "clicked_sim2",
  "compromised_sim0", "compromised_sim05", "compromised_sim1", "compromised_sim2",
  "reported_sim1", "reported_sim2",
  "clicked", "compromised", "reported",
  "optimism_bias", "risk_perception", "negative_emotions",
  "acceptance", "self_efficacy", "locus_of_control", "training_intention"
)

# check classes
sapply(vars_to_check, \(v) paste(class(df_analysis_filt[[v]]), collapse = ","))

# Histograms + skewness 
par(mfrow = c(3, 3))  

for (var in vars_to_check) {
  x <- df_analysis_filt[[var]]
  if (is.logical(x)) x <- as.integer(x)  

  hist(x,
       main = paste("Histogram of", var),
       xlab = var,
       col = "lightblue",
       breaks = 20,
       border = "white")

  cat("Variable:", var, "\n")
  cat("  Skewness :", round(skewness(x, na.rm = TRUE), 2), "\n")
  cat("  Kurtosis :", round(kurtosis(x, na.rm = TRUE), 2), "\n\n")
}

par(mfrow = c(1, 1)) 


## 2) Linearity check: Training intention vs each predictor ----
##    (Scatter + lm smoother)

predictors <- c(
  "clicked_sim1",
  "optimism_bias",
  "risk_perception",
  "negative_emotions",
  "acceptance",
  "self_efficacy",
  "locus_of_control",
  "years_org_num"
)

outcome <- "training_intention"

plot_list <- lapply(predictors, function(var) {
  ggplot(df_analysis_filt, aes_string(x = var, y = outcome)) +
    geom_point(alpha = 0.4) +
    geom_smooth(method = "lm", se = FALSE) +
    theme_minimal() +
    labs(
      title = paste("Training Intention ~", var),
      x = var,
      y = "Training Intention"
    )
})

wrap_plots(plot_list, ncol = 3)


## 3) Missing data and imputation (mice)

model_vars <- c(
  "training_intention",
  "optimism_bias",
  "risk_perception",
  "negative_emotions",
  "acceptance",
  "self_efficacy",
  "locus_of_control",
  "years_org_num"
)

df_sub <- df_analysis_filt[, model_vars]


imp <- mice(df_sub, method = "pmm", m = 5, seed = 123)


model_imp <- with(
  imp,
  lm(training_intention ~ optimism_bias + risk_perception +
       negative_emotions + acceptance + self_efficacy + locus_of_control +
       years_org_num)
)

cat("\nPooled results after MI:\n")
print(summary(pool(model_imp)))


## 4) Single completed dataset model------


df_complete1 <- complete(imp, 1)

lm_single <- lm(
  training_intention ~ optimism_bias + risk_perception +
    negative_emotions + acceptance + self_efficacy + locus_of_control +
    years_org_num,
  data = df_complete1
)

cat("\nModel summary on completed dataset 1:\n")
print(summary(lm_single))


## 5) Assumption tests on lm_single ----------------------------
##    5a Heteroskedasticity (Breusch-Pagan)
##    5b Multicollinearity (VIF)
##    5c Independence of residuals (Durbin-Watson)
##    5d Influence / Outliers (Cook's distance)

# 5a) Heteroskedasticity
cat("\nBreusch-Pagan test (heteroskedasticity):\n")
print(bptest(lm_single))

# 5b) Multicollinearity
cat("\nVariance Inflation Factors (VIF):\n")
print(vif(lm_single))

# 5c) Autocorrelation / Independence
cat("\nDurbin-Watson test (residual independence):\n")
print(dwtest(lm_single))

# 5d) Cook's distance plot
plot(cooks.distance(lm_single), type = "h",
     main = "Cook's Distance",
     ylab = "Cook's D")
abline(h = 4 / nrow(df_complete1), col = "red", lty = 2)


```










#Hypothesis 1: Level of compromise
```{r}


## -------------------------------------------------
## Mediation: level_compromised_sim1 → Mediatoren → level_compromised_sim2
## -------------------------------------------------
df_analysis_filt <- df_analysis_filt %>%
  mutate(
   
    Gender = factor(Gender),
    age = factor(
      Age,
      levels = c("18-24", "25-34", "35-44", "45-54", "55-64", "65+"),
      ordered = TRUE
    ),
    age_num = as.numeric(age),

    gender_bin = case_when(
      tolower(as.character(Gender)) %in% c("female", "f", "weiblich") ~ 1,
      tolower(as.character(Gender)) %in% c("male", "m", "männlich")   ~ 0,
      TRUE ~ NA_real_
    ),

  
    jobrole_bin01 = ifelse(JobRole_bin == "non-academic", 1, 0),

    clicked_sim1     = as.numeric(clicked_sim1),
    clicked_sim2     = as.numeric(clicked_sim2),
    compromised_sim1 = as.numeric(compromised_sim1),
    compromised_sim2 = as.numeric(compromised_sim2),

    level_compromised_sim1 = case_when(
      compromised_sim1 == 1 ~ 2L,
      clicked_sim1     == 1 ~ 1L,
      TRUE                  ~ 0L
    ),
    level_compromised_sim2 = case_when(
      compromised_sim2 == 1 ~ 2L,
      clicked_sim2     == 1 ~ 1L,
      TRUE                  ~ 0L
    )
  )

table(
  JobRole = ifelse(df_analysis$jobrole_bin01 == 1,
                   "Non-academic",
                   "Academic")
)





## -------------------------------------------------
## Mediation: level_compromised_sim1 → Mediatoren → level_compromised_sim2
## -------------------------------------------------
df_analysis_filt <- df_analysis_filt %>%
  mutate(
    Gender = factor(Gender),

    age = factor(
      Age,
      levels = c("18-24", "25-34", "35-44", "45-54", "55-64", "65+"),
      ordered = TRUE
    ),
    age_num = as.numeric(age),

    gender_bin = case_when(
      tolower(as.character(Gender)) %in% c("female", "f", "weiblich") ~ 1,
      tolower(as.character(Gender)) %in% c("male", "m", "männlich")   ~ 0,
      TRUE ~ NA_real_
    ),

    jobrole_bin01 = ifelse(JobRole_bin == "non-academic", 1, 0),

    clicked_sim1     = as.numeric(clicked_sim1),
    clicked_sim2     = as.numeric(clicked_sim2),
    compromised_sim1 = as.numeric(compromised_sim1),
    compromised_sim2 = as.numeric(compromised_sim2),

    level_compromised_sim1 = case_when(
      compromised_sim1 == 1 ~ 2L,
      clicked_sim1     == 1 ~ 1L,
      TRUE                  ~ 0L
    ),
    level_compromised_sim2 = case_when(
      compromised_sim2 == 1 ~ 2L,
      clicked_sim2     == 1 ~ 1L,
      TRUE                  ~ 0L
    )
  )


## -------------------------------------------------
## SEM-Model
## -------------------------------------------------

med_model21_job <- '
  # predictor (sim1) to mediator
  optimism_bias     ~ a1*level_compromised_sim1 + age_num + gender_bin + jobrole_bin01 + years_org_num
  risk_perception   ~ a2*level_compromised_sim1 + age_num + gender_bin + jobrole_bin01 + years_org_num
  negative_emotions ~ a3*level_compromised_sim1 + age_num + gender_bin + jobrole_bin01 + years_org_num
  acceptance        ~ a4*level_compromised_sim1 + age_num + gender_bin + jobrole_bin01 + years_org_num
  self_efficacy     ~ a5*level_compromised_sim1 + age_num + gender_bin + jobrole_bin01 + years_org_num
  locus_of_control  ~ a6*level_compromised_sim1 + age_num + gender_bin + jobrole_bin01 + years_org_num

  # outcome (sim2)
  level_compromised_sim2 ~ c3*level_compromised_sim1 +
                           b1*optimism_bias + b2*risk_perception +
                           b3*negative_emotions + b4*acceptance +
                           b5*self_efficacy + b6*locus_of_control +
                           age_num + gender_bin + jobrole_bin01 + years_org_num

  # indirect effects
  ind1 := a1*b1
  ind2 := a2*b2
  ind3 := a3*b3
  ind4 := a4*b4
  ind5 := a5*b5
  ind6 := a6*b6
  ind_total := ind1 + ind2 + ind3 + ind4 + ind5 + ind6

  # total effect
  total := c3 + ind_total
'


## -------------------------------------------------
## Model fit
## -------------------------------------------------

fit_mediation_job <- sem(
  med_model21_job,
  data = df_analysis_filt,
  estimator = "MLR",
  missing = "ML",
  meanstructure = TRUE
)

summary(fit_mediation_job, standardized = TRUE, fit.measures = TRUE, rsquare = TRUE)



# ----------------------------------------
# Simple direct model (linear, no mediation)
# ----------------------------------------

df_direct <- df_analysis_filt %>%
  mutate(
    lvl1 = as.numeric(level_compromised_sim1),
    lvl2 = as.numeric(level_compromised_sim2)
  )

fit_direct_beta <- lm(
  scale(lvl2) ~ scale(lvl1) + scale(age_num) + gender_bin +
    jobrole_bin01 + scale(years_org_num),
  data = df_direct
)

summary(fit_direct_beta)




```





#Post Hoc H1: McNemar

```{r}
## -------------------------------------------------
## 1) Change between Simulation 1 and 2 (paired analysis)
## -------------------------------------------------


cat("Clicked:\n")
df_pair <- df_analysis_filt %>%
  filter(!is.na(clicked_sim1) & !is.na(clicked_sim2))

pct_click1 <- mean(df_pair$clicked_sim1, na.rm = TRUE) * 100
pct_click2 <- mean(df_pair$clicked_sim2, na.rm = TRUE) * 100
cat(sprintf("Click rates: Sim1 = %.1f%%, Sim2 = %.1f%%\n", pct_click1, pct_click2))

tab_click <- table(df_pair$clicked_sim1, df_pair$clicked_sim2)
print(tab_click)
mcnemar_click <- mcnemar.test(tab_click)
cat("McNemar test for clicks (Sim1 vs Sim2):\n")
print(mcnemar_click)


cat("Compromised:\n")
df_pair_comp <- df_analysis_filt %>%
  filter(!is.na(compromised_sim1) & !is.na(compromised_sim2))

pct_comp1 <- mean(df_pair_comp$compromised_sim1, na.rm = TRUE) * 100
pct_comp2 <- mean(df_pair_comp$compromised_sim2, na.rm = TRUE) * 100
cat(sprintf("Compromise rates: Sim1 = %.1f%%, Sim2 = %.1f%%\n", pct_comp1, pct_comp2))

tab_comp <- table(df_pair_comp$compromised_sim1, df_pair_comp$compromised_sim2)
print(tab_comp)
mcnemar_comp <- mcnemar.test(tab_comp)
cat("McNemar test for compromises (Sim1 vs Sim2):\n")
print(mcnemar_comp)



## -------------------------------------------------
## 2) Pairwise test across all four simulation cycles (descriptive + Cochran-Armitage test)
##    For testing if there is a significant trend over time
## -------------------------------------------------


count_yes  <- function(x) sum(x == 1, na.rm = TRUE)
count_no   <- function(x) sum(x == 0, na.rm = TRUE)
denom_N    <- function(x) sum(!is.na(x))


click_counts <- tibble(
  sim    = c("sim0","sim0.5","sim1","sim2"),
  yes    = c(count_yes(df_analysis_filt$clicked_sim0),
             count_yes(df_analysis_filt$clicked_sim05),
             count_yes(df_analysis_filt$clicked_sim1),
             count_yes(df_analysis_filt$clicked_sim2)),
  no     = c(count_no(df_analysis_filt$clicked_sim0),
             count_no(df_analysis_filt$clicked_sim05),
             count_no(df_analysis_filt$clicked_sim1),
             count_no(df_analysis_filt$clicked_sim2))
) %>%
  mutate(
    denom = yes + no,
    pct   = round(100 * yes / denom, 1)
  )

comp_counts <- tibble(
  sim    = c("sim0","sim0.5","sim1","sim2"),
  yes    = c(count_yes(df_analysis_filt$compromised_sim0),
             count_yes(df_analysis_filt$compromised_sim05),
             count_yes(df_analysis_filt$compromised_sim1),
             count_yes(df_analysis_filt$compromised_sim2)),
  no     = c(count_no(df_analysis_filt$compromised_sim0),
             count_no(df_analysis_filt$compromised_sim05),
             count_no(df_analysis_filt$compromised_sim1),
             count_no(df_analysis_filt$compromised_sim2))
) %>%
  mutate(
    denom = yes + no,
    pct   = round(100 * yes / denom, 1)
  )

cat("\nClick rates by simulation:\n")
print(click_counts)

cat("\nCompromise rates by simulation:\n")
print(comp_counts)


pairwise_prop_test <- function(df_counts, label){
  sims <- df_counts$sim
  for(i in 1:(nrow(df_counts)-1)){
    s1 <- df_counts[i, ]
    s2 <- df_counts[i+1, ]
    cat("\n", label, ": ", s1$sim, " vs ", s2$sim, "\n", sep = "")
    
    print(
      prop.test(
        x = c(s1$yes, s2$yes),
        n = c(s1$denom, s2$denom),
        alternative = "less"  
      )
    )
  }
}

cat("\n--- Pairwise tests for CLICK ---\n")
pairwise_prop_test(click_counts, "Click")

cat("\n--- Pairwise tests for COMPROMISE ---\n")
pairwise_prop_test(comp_counts, "Compromise")



##---------------
##Combined
##---------------
library(ggplot2)
library(dplyr)

rates_long <- bind_rows(
  click_counts %>% mutate(metric = "Click"),
  comp_counts  %>% mutate(metric = "Compromise")
) %>%
  mutate(
    sim_label = dplyr::recode(
      sim,
      "sim0"   = "Simulation 1",
      "sim0.5" = "Simulation 2",
      "sim1"   = "Simulation 3",
      "sim2"   = "Simulation 4"
    )
  )


p_both_usenix <- ggplot(
  rates_long,
  aes(x = sim_label, y = pct, group = metric, color = metric)
) +
  geom_line(linewidth = 0.6) +
  geom_point(size = 1.8) +
  scale_color_manual(
    values = c(
      "Click" = "steelblue",       # blau
      "Compromise" = "firebrick"   # rot
    )
  ) +
  scale_y_continuous(
    limits = c(0, NA),
    expand = expansion(mult = c(0, 0.04))
  ) +
  labs(
    x = "Simulation",
    y = "Rate (%)",
    color = NULL
  ) +
  theme_classic(base_size = 10) +
  theme(
    plot.title = element_blank(),

    axis.text.x = element_text(size = 11, margin = margin(t = 4)),
    axis.text.y = element_text(size = 11),

    axis.line = element_line(linewidth = 0.8),
    axis.ticks = element_line(linewidth = 0.8),

    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.box = "horizontal",
    legend.title = element_blank(),
    legend.text = element_text(size = 10),

    legend.margin = margin(t = 0, r = 0, b = 0, l = 0),
    legend.box.margin = margin(t = -6, r = 0, b = -6, l = 0),
    plot.margin = margin(5, 5, 2, 5),

    legend.background = element_blank(),
    legend.key = element_blank()
  )

ggsave(
  "phishing_rates_combined_usenix.pdf",
  plot = p_both_usenix,
  width = 6,
  height = 4,
  units = "in",
  device = cairo_pdf
)



```


#Hypothesis 2: Cybersecurity training intention

```{r}



df_analysis_filt <- df_analysis_filt %>%
  mutate(
    cybsafeLinkClicked = as.numeric(cybsafeLinkClicked),
    training_intention = as.numeric(training_intention)
  )

## -------------------------------------------------
## H2a: Mediation model with training_intention as outcome
## -------------------------------------------------

model_H3a <- '
  # a-paths: predictor -> mediators
  optimism_bias     ~ a1*level_compromised_sim1 + age_num + gender_bin + jobrole_bin01 + years_org_num
  risk_perception   ~ a2*level_compromised_sim1 + age_num + gender_bin + jobrole_bin01 + years_org_num
  negative_emotions ~ a3*level_compromised_sim1 + age_num + gender_bin + jobrole_bin01 + years_org_num
  acceptance        ~ a4*level_compromised_sim1 + age_num + gender_bin + jobrole_bin01 + years_org_num
  self_efficacy     ~ a5*level_compromised_sim1 + age_num + gender_bin + jobrole_bin01 + years_org_num
  locus_of_control  ~ a6*level_compromised_sim1 + age_num + gender_bin + jobrole_bin01 + years_org_num

  # b-paths + direct path
  training_intention ~ c3*level_compromised_sim1 +
                       b1*optimism_bias +
                       b2*risk_perception +
                       b3*negative_emotions +
                       b4*acceptance +
                       b5*self_efficacy +
                       b6*locus_of_control +
                       age_num + gender_bin + jobrole_bin01 + years_org_num

  # indirect effects
  ind1 := a1*b1
  ind2 := a2*b2
  ind3 := a3*b3
  ind4 := a4*b4
  ind5 := a5*b5
  ind6 := a6*b6

  ind_total := ind1 + ind2 + ind3 + ind4 + ind5 + ind6
  total_effect := c3 + ind_total
'


fit_H3a <- sem(
  model_H3a,
  data = df_analysis_filt,
  estimator = "MLR",     
  missing   = "ML",       
  meanstructure = TRUE,
  fixed.x = FALSE
)

summary(
  fit_H3a,
  standardized = TRUE,
  fit.measures = TRUE,
  rsquare = TRUE
)


## -------------------------------------------------
## Post Hoc H2: Descriptives: uptake of training / cybsafeLinkClicked
## -------------------------------------------------

N_total <- nrow(df_analysis_filt)


N_observed <- sum(!is.na(df_analysis_filt$cybsafeLinkClicked))


N_clicked <- sum(df_analysis_filt$cybsafeLinkClicked == 1, na.rm = TRUE)

pct_of_total    <- round(100 * N_clicked / N_total, 1)
pct_of_observed <- round(100 * N_clicked / N_observed, 1)

cat("\nTraining uptake summary:\n")
cat(" Total N in df_analysis_filt:         ", N_total, "\n")
cat(" N who clicked training link:    ", N_clicked, "\n")
cat(" % of FULL sample:               ", pct_of_total, "%\n")


df_analysis_filt <- df_analysis_filt %>%
  mutate(
    cybsafeLinkClicked = as.numeric(cybsafeLinkClicked),
    training_intention = as.numeric(training_intention)
  )

mod_biv <- glm(
  cybsafeLinkClicked ~ training_intention + age_num + gender_bin +
    jobrole_bin01 + years_org_num,
  data = df_analysis_filt,
  family = binomial
)

summary(mod_biv)




##----------------
##Sensitivity check
##----------------

model_H3a_cov <- paste0(
  model_H3a,
  '
  optimism_bias ~~ risk_perception + negative_emotions +
                   acceptance + self_efficacy + locus_of_control

  risk_perception ~~ negative_emotions + acceptance +
                     self_efficacy + locus_of_control

  negative_emotions ~~ acceptance + self_efficacy +
                       locus_of_control

  acceptance ~~ self_efficacy + locus_of_control

  self_efficacy ~~ locus_of_control
  '
)

fit_H3a_cov <- sem(
  model_H3a_cov,
  data = df_analysis_filt,
  estimator = "MLR",
  missing = "ML",
  meanstructure = TRUE,
  fixed.x = FALSE
)



```

#H3: Personality Level Repeat Clicker (30 Imputations)

```{r}
library(dplyr)
library(mice)

## ----------------------------
## Helpers
## ----------------------------


to_delivered <- function(x) {
  x <- trimws(as.character(x))
  dplyr::case_when(
    is.na(x) | x == "" ~ 0L,
    x == "--"          ~ 0L,
    TRUE               ~ 1L
  )
}


to_clicked <- function(x) {
  x <- trimws(as.character(x))
  dplyr::case_when(
    is.na(x) | x == "" ~ 0L,
    x == "--"          ~ 0L,
    TRUE               ~ 1L
  )
}

## ----------------------------
## 1) Build analysis variables
## ----------------------------

df_analysis_filt <- df_analysis_filt %>%
  mutate(
   
    Gender = factor(Gender),
    age = factor(
      Age,
      levels = c("18-24", "25-34", "35-44", "45-54", "55-64", "65+"),
      ordered = TRUE
    ),
    age_num = as.numeric(age),

    gender_bin = case_when(
      tolower(as.character(Gender)) %in% c("female", "f", "weiblich") ~ 1,
      tolower(as.character(Gender)) %in% c("male", "m", "männlich")   ~ 0,
      TRUE ~ NA_real_
    ),

    
    JobRole_bin = as.factor(JobRole_bin),

    
    sent_sim0  = to_delivered(`sim0_Opened_Time_c1_2023-03-29`),
    sent_sim05 = to_delivered(`sim0.5_Opened_Time_c2_2024-07-22`),

    
    sent_sim1 = to_delivered(sim1_SuccessfullyDeliveredEmail_TimeStamp),
    sent_sim2 = to_delivered(sim2_SuccessfullyDeliveredEmail_TimeStamp),


    # CLICKED
    clicked_sim0  = to_clicked(`sim0_Viewed Landing Page_Time_c1_2023-03-29`),
    clicked_sim05 = to_clicked(`sim0.5_Viewed Landing Page_Time_c2_2024-07-22`),
    clicked_sim1  = to_clicked(sim1_EmailLinkClicked_TimeStamp),
    clicked_sim2  = to_clicked(sim2_EmailLinkClicked_TimeStamp)
  ) %>%
  
  mutate(
    clicked_sim0  = clicked_sim0  * sent_sim0,
    clicked_sim05 = clicked_sim05 * sent_sim05,
    clicked_sim1  = clicked_sim1  * sent_sim1,
    clicked_sim2  = clicked_sim2  * sent_sim2
  ) %>%
  mutate(
    n_sent    = sent_sim0 + sent_sim05 + sent_sim1 + sent_sim2,
    n_clicked = clicked_sim0 + clicked_sim05 + clicked_sim1 + clicked_sim2,
    click_rate = if_else(n_sent > 0, n_clicked / n_sent, NA_real_)
  )


sum(df_analysis_filt$n_clicked > df_analysis_filt$n_sent, na.rm = TRUE)


df_analysis_filt <- df_analysis_filt %>%
  mutate(
    repeat_clicker = case_when(
      n_sent < 3 ~ NA_integer_,
      n_clicked >= 2 ~ 1L,
      TRUE ~ 0L
    )
  )

table(df_analysis_filt$repeat_clicker, useNA = "ifany")

## ----------------------------
## 2) Complete exposure subset (4/4)
## ----------------------------

df_cc4 <- df_analysis_filt %>%
  filter(sent_sim0 == 1, sent_sim05 == 1, sent_sim1 == 1, sent_sim2 == 1) %>%
  mutate(
    n_sent = 4L,
    n_clicked = clicked_sim0 + clicked_sim05 + clicked_sim1 + clicked_sim2
  )

cat("N mit vollständigem Exposure (4/4):", nrow(df_cc4), "\n")

## ----------------------------
## 3) Imputation dataset (predictors only)
##    age_num, gender_bin, JobRole_bin, years_org_num NICHT imputieren
## ----------------------------

dat_imp <- df_cc4 %>%
  dplyr::select(
    n_clicked,          
    optimism_bias,
    self_efficacy,
    risk_perception,
    locus_of_control,
    acceptance,
    negative_emotions,
    age_num,            
    gender_bin,         
    JobRole_bin,
    years_org_num
  )

meth <- make.method(dat_imp)


meth["n_clicked"] <- ""


meth[c("age_num", "gender_bin", "JobRole_bin", "years_org_num")] <- ""


meth[c(
  "optimism_bias",
  "self_efficacy",
  "risk_perception",
  "locus_of_control",
  "acceptance",
  "negative_emotions"
)] <- "pmm"

pred <- make.predictorMatrix(dat_imp)
pred[,] <- 1
diag(pred) <- 0


pred["n_clicked", ] <- 0




set.seed(123)
imp <- mice(
  dat_imp,
  m = 30,
  method = meth,
  predictorMatrix = pred,
  maxit = 30
  
)


zvars <- c("optimism_bias","self_efficacy","risk_perception",
           "locus_of_control","acceptance","negative_emotions","age_num",
           "years_org_num")

fit_imp_z <- with(
  imp,
  {
    d <- data.frame(n_clicked, optimism_bias, self_efficacy, risk_perception,
                    locus_of_control, acceptance, negative_emotions,
                    age_num, gender_bin, JobRole_bin, years_org_num)

    for (v in intersect(zvars, names(d))) {
      d[[v]] <- as.numeric(scale(d[[v]]))
    }

    glm(
      cbind(n_clicked, 4 - n_clicked) ~
        optimism_bias + self_efficacy + risk_perception +
        locus_of_control + acceptance + negative_emotions +
        age_num + gender_bin + JobRole_bin + years_org_num,
      family = binomial(),
      data = d
    )
  }
)

res_z <- pool(fit_imp_z)
summary(res_z)


sum_z <- summary(res_z)

sum_z$OR        <- exp(sum_z$estimate)
sum_z$OR_low95  <- exp(sum_z$estimate - 1.96 * sum_z$std.error)
sum_z$OR_high95 <- exp(sum_z$estimate + 1.96 * sum_z$std.error)

sum_z[, c("term","estimate","std.error","p.value","OR","OR_low95","OR_high95")]



## ============================================================
##  forest plot 
## ============================================================

df_plot_manual <- tibble::tribble(
  ~Predictor, ~beta, ~SE, ~OR, ~OR_low, ~OR_high,
  "Optimism bias",        0.49, 0.20, 1.64, 1.10, 2.43,
  "Self-efficacy",       -0.26, 0.25, 0.77, 0.47, 1.25,
  "Risk perception",     -0.17, 0.14, 0.85, 0.65, 1.10,
  "Locus of control",    -0.24, 0.17, 0.79, 0.57, 1.09,
  "Acceptance",           0.14, 0.14, 1.15, 0.87, 1.52,
  "Negative emotions",    0.01, 0.12, 1.01, 0.79, 1.28
) %>%
  mutate(
    sig = (OR_low > 1) | (OR_high < 1),
    Predictor = factor(Predictor, levels = Predictor[order(OR, decreasing = TRUE)]))



p <- ggplot(df_plot_manual, aes(x = OR, y = Predictor)) +
  geom_vline(xintercept = 1, linetype = "dashed",
             linewidth = 0.7, color = "grey40") +
  geom_errorbarh(
    aes(xmin = OR_low, xmax = OR_high),
    height = 0.20,
    linewidth = 0.8,
    color = "grey30"
  ) +
  geom_point(
    aes(fill = sig),
    shape = 21,
    size = 3.6,
    color = "black"
  ) +
  scale_fill_manual(
    values = c(`TRUE` = "black", `FALSE` = "white"),
    guide = "none"
  ) +
  scale_x_log10(
    breaks = c(0.5, 0.75, 1, 1.25, 1.5, 2, 3),
    labels = c("0.5","0.75","1","1.25","1.5","2","3")
  ) +
  scale_y_discrete(limits = rev) +   
  labs(
    x = "Odds ratio (log scale) with 95% CI",
    y = NULL
  ) +
  theme_classic(base_size = 14) +
  theme(
    axis.text.y  = element_text(size = 15),
    axis.text.x  = element_text(size = 13),
    axis.title.x = element_text(size = 14),
    axis.line.y  = element_blank(),
    axis.ticks.y = element_blank(),
    plot.margin  = margin(10, 15, 10, 10)
  )

print(p)


ggsave(
  "forest_plot_odds_ratios.pdf",
  plot   = p,
  width  = 7,
  height = 4.5,
  units  = "in",
  device = cairo_pdf
)

##----------------------
##Histogram click sums and compromise probability
##----------------------

local({

  library(dplyr)
  library(tidyr)
  library(ggplot2)

 

  to_binary_present <- function(x) {
    x <- trimws(as.character(x))
    dplyr::case_when(
      is.na(x) | x == "" ~ 0L,
      x == "--"          ~ 0L,
      TRUE               ~ 1L
    )
  }

 
  to_clicked <- function(x) {
    x <- trimws(as.character(x))
    dplyr::case_when(
      is.na(x) | x == "" ~ 0L,
      x == "--"          ~ 0L,
      TRUE               ~ 1L
    )
  }

  
  wilson_ci <- function(x, n, z = 1.96) {
    if (n == 0) return(c(NA_real_, NA_real_))
    p <- x / n
    denom <- 1 + z^2 / n
    center <- (p + z^2/(2*n)) / denom
    half <- (z * sqrt((p*(1-p) + z^2/(4*n)) / n)) / denom
    c(center - half, center + half)
  }

  ## ----------------------------
  ## 1) Build per-person variables
  ## ----------------------------

  dat0 <- df_analysis_filt %>%
    mutate(
      
      sent_sim0  = to_binary_present(`sim0_Opened_Time_c1_2023-03-29`),
      sent_sim05 = to_binary_present(`sim0.5_Opened_Time_c2_2024-07-22`),
      sent_sim1  = to_binary_present(sim1_SuccessfullyDeliveredEmail_TimeStamp),
      sent_sim2  = to_binary_present(sim2_SuccessfullyDeliveredEmail_TimeStamp),

      
      clicked_sim0  = to_clicked(`sim0_Viewed Landing Page_Time_c1_2023-03-29`),
      clicked_sim05 = to_clicked(`sim0.5_Viewed Landing Page_Time_c2_2024-07-22`),
      clicked_sim1  = to_clicked(sim1_EmailLinkClicked_TimeStamp),
      clicked_sim2  = to_clicked(sim2_EmailLinkClicked_TimeStamp),

      
      clicked_sim0  = clicked_sim0  * sent_sim0,
      clicked_sim05 = clicked_sim05 * sent_sim05,
      clicked_sim1  = clicked_sim1  * sent_sim1,
      clicked_sim2  = clicked_sim2  * sent_sim2,

     
      compromised_sim0  = to_binary_present(`sim0_Data Entered_Time_c1_2023-03-29`),
      compromised_sim05 = to_binary_present(`sim0.5_Data Entered_Time_c2_2024-07-22`),
      compromised_sim1  = to_binary_present(sim1_CredSupplied_TimeStamp_Compromised),
      compromised_sim2  = to_binary_present(sim2_CredSupplied_TimeStamp_Compromised),

      
      compromised_sim0  = compromised_sim0  * sent_sim0,
      compromised_sim05 = compromised_sim05 * sent_sim05,
      compromised_sim1  = compromised_sim1  * sent_sim1,
      compromised_sim2  = compromised_sim2  * sent_sim2
    ) %>%
    mutate(
      n_sent = sent_sim0 + sent_sim05 + sent_sim1 + sent_sim2,
      n_clicked = clicked_sim0 + clicked_sim05 + clicked_sim1 + clicked_sim2,
      n_compromised = compromised_sim0 + compromised_sim05 + compromised_sim1 + compromised_sim2,
      any_compromise = if_else(n_compromised >= 1, "Compromised (>=1)", "Not compromised")
    )

  
  df_cc4 <- dat0 %>%
    filter(sent_sim0 == 1, sent_sim05 == 1, sent_sim1 == 1, sent_sim2 == 1) %>%
    mutate(n_sent = 4L)

  cat("N complete exposure (4/4):", nrow(df_cc4), "\n")

library(dplyr)
library(ggplot2)


wilson_ci <- function(x, n, z = 1.96) {
  if (is.na(n) || n == 0) return(c(NA_real_, NA_real_))
  p <- x / n
  denom <- 1 + z^2 / n
  center <- (p + z^2/(2*n)) / denom
  half <- (z * sqrt((p*(1-p) + z^2/(4*n)) / n)) / denom
  c(center - half, center + half)
}

sumdat <- df_cc4 %>%
  filter(n_clicked >= 1) %>%             
  group_by(n_clicked) %>%
  summarise(
    n_people = n(),
    clicks_total = sum(n_clicked, na.rm = TRUE),
    comp_total   = sum(n_compromised, na.rm = TRUE),
    rate_comp_per_click = comp_total / clicks_total,
    ci_low  = wilson_ci(comp_total, clicks_total)[1],
    ci_high = wilson_ci(comp_total, clicks_total)[2],
    .groups = "drop"
  )


k <- max(sumdat$n_people)

p <- ggplot(sumdat, aes(x = factor(n_clicked))) +
  
  geom_col(aes(y = n_people), fill = "grey40", color = "white") +

  
  geom_line(aes(y = rate_comp_per_click * k, group = 1), linewidth = 0.8) +
  geom_point(aes(y = rate_comp_per_click * k), size = 3) +

 
  geom_errorbar(
    aes(ymin = ci_low * k, ymax = ci_high * k),
    width = 0.10
  ) +

  scale_y_continuous(
    name = "Number of participants",
    sec.axis = sec_axis(~ . / k, name = "Compromise probability per click")
  ) +
  labs(x = "Number of phishing emails clicked (1–4)") +
  theme_classic(base_size = 16)

p

ggsave(
  "clickcount_with_compromise_per_click_overlay.pdf",
  plot = p, width = 6, height = 4, device = cairo_pdf
)

})

#####NEW

library(mice)
library(dplyr)

# ------------------------------------------------------------
# H3 donor-pool sensitivity analysis
# ------------------------------------------------------------

run_donor_sensitivity <- function(k) {

  # Nur die Anzahl der PMM-Donoren wird verändert
  imp_k <- mice(
    dat_imp,
    m = 100,
    method = meth,
    predictorMatrix = pred,
    maxit = 30,
    donors = k,
    seed = 123,
    printFlag = FALSE
  )

  # Identisches H3-Modell wie in der Hauptanalyse
  fit_k <- with(
    imp_k,
    {
      d <- data.frame(
        n_clicked,
        optimism_bias,
        self_efficacy,
        risk_perception,
        locus_of_control,
        acceptance,
        negative_emotions,
        age_num,
        gender_bin,
        JobRole_bin,
        years_org_num
      )

      # Identische Standardisierung wie in der Hauptanalyse
      for (v in intersect(zvars, names(d))) {
        d[[v]] <- as.numeric(scale(d[[v]]))
      }

      glm(
        cbind(n_clicked, 4 - n_clicked) ~
          optimism_bias +
          self_efficacy +
          risk_perception +
          locus_of_control +
          acceptance +
          negative_emotions +
          age_num +
          gender_bin +
          JobRole_bin +
          years_org_num,
        family = binomial(),
        data = d
      )
    }
  )

  # Pooling nach Rubin
  pooled_k <- summary(pool(fit_k))

  # Konfidenzintervalle und Odds Ratios
  pooled_k |>
    mutate(
      donors = k,
      critical_value = qt(.975, df),
      CI_low  = estimate - critical_value * std.error,
      CI_high = estimate + critical_value * std.error,
      OR = exp(estimate),
      OR_low95 = exp(CI_low),
      OR_high95 = exp(CI_high)
    )
}

# Donorpool-Größen vergleichen
donor_results <- bind_rows(
  lapply(c(1, 3, 5), run_donor_sensitivity)
)

# Ergebnisse für Optimism Bias
optimism_donor_results <- donor_results |>
  filter(term == "optimism_bias") |>
  select(
    donors,
    estimate,
    std.error,
    statistic,
    df,
    p.value,
    CI_low,
    CI_high,
    OR,
    OR_low95,
    OR_high95
  )

print(optimism_donor_results)

donor_results |>
  select(
    donors,
    term,
    estimate,
    std.error,
    p.value,
    CI_low,
    CI_high
  ) |>
  arrange(term, donors) |>
  tibble::as_tibble() |>
  print(n = Inf)
```



#H3: Personality Level Repeat Clicker (100 Imputations, Donor pools 1,3 and 5)

```{r}
library(dplyr)
library(mice)

## ----------------------------
## Helpers
## ----------------------------


to_delivered <- function(x) {
  x <- trimws(as.character(x))
  dplyr::case_when(
    is.na(x) | x == "" ~ 0L,
    x == "--"          ~ 0L,
    TRUE               ~ 1L
  )
}


to_clicked <- function(x) {
  x <- trimws(as.character(x))
  dplyr::case_when(
    is.na(x) | x == "" ~ 0L,
    x == "--"          ~ 0L,
    TRUE               ~ 1L
  )
}

## ----------------------------
## 1) Build analysis variables
## ----------------------------

df_analysis_filt <- df_analysis_filt %>%
  mutate(
   
    Gender = factor(Gender),
    age = factor(
      Age,
      levels = c("18-24", "25-34", "35-44", "45-54", "55-64", "65+"),
      ordered = TRUE
    ),
    age_num = as.numeric(age),

    gender_bin = case_when(
      tolower(as.character(Gender)) %in% c("female", "f", "weiblich") ~ 1,
      tolower(as.character(Gender)) %in% c("male", "m", "männlich")   ~ 0,
      TRUE ~ NA_real_
    ),

    
    JobRole_bin = as.factor(JobRole_bin),

    
    sent_sim0  = to_delivered(`sim0_Opened_Time_c1_2023-03-29`),
    sent_sim05 = to_delivered(`sim0.5_Opened_Time_c2_2024-07-22`),

    
    sent_sim1 = to_delivered(sim1_SuccessfullyDeliveredEmail_TimeStamp),
    sent_sim2 = to_delivered(sim2_SuccessfullyDeliveredEmail_TimeStamp),


    # CLICKED
    clicked_sim0  = to_clicked(`sim0_Viewed Landing Page_Time_c1_2023-03-29`),
    clicked_sim05 = to_clicked(`sim0.5_Viewed Landing Page_Time_c2_2024-07-22`),
    clicked_sim1  = to_clicked(sim1_EmailLinkClicked_TimeStamp),
    clicked_sim2  = to_clicked(sim2_EmailLinkClicked_TimeStamp)
  ) %>%
  
  mutate(
    clicked_sim0  = clicked_sim0  * sent_sim0,
    clicked_sim05 = clicked_sim05 * sent_sim05,
    clicked_sim1  = clicked_sim1  * sent_sim1,
    clicked_sim2  = clicked_sim2  * sent_sim2
  ) %>%
  mutate(
    n_sent    = sent_sim0 + sent_sim05 + sent_sim1 + sent_sim2,
    n_clicked = clicked_sim0 + clicked_sim05 + clicked_sim1 + clicked_sim2,
    click_rate = if_else(n_sent > 0, n_clicked / n_sent, NA_real_)
  )


sum(df_analysis_filt$n_clicked > df_analysis_filt$n_sent, na.rm = TRUE)


df_analysis_filt <- df_analysis_filt %>%
  mutate(
    repeat_clicker = case_when(
      n_sent < 3 ~ NA_integer_,
      n_clicked >= 2 ~ 1L,
      TRUE ~ 0L
    )
  )

table(df_analysis_filt$repeat_clicker, useNA = "ifany")

## ----------------------------
## 2) Complete exposure subset (4/4)
## ----------------------------

df_cc4 <- df_analysis_filt %>%
  filter(sent_sim0 == 1, sent_sim05 == 1, sent_sim1 == 1, sent_sim2 == 1) %>%
  mutate(
    n_sent = 4L,
    n_clicked = clicked_sim0 + clicked_sim05 + clicked_sim1 + clicked_sim2
  )

cat("N mit vollständigem Exposure (4/4):", nrow(df_cc4), "\n")

## ----------------------------
## 3) Imputation dataset (predictors only)
##    age_num, gender_bin, JobRole_bin, years_org_num NICHT imputieren
## ----------------------------

dat_imp <- df_cc4 %>%
  dplyr::select(
    n_clicked,          
    optimism_bias,
    self_efficacy,
    risk_perception,
    locus_of_control,
    acceptance,
    negative_emotions,
    age_num,            
    gender_bin,         
    JobRole_bin,
    years_org_num
  )

meth <- make.method(dat_imp)


meth["n_clicked"] <- ""


meth[c("age_num", "gender_bin", "JobRole_bin", "years_org_num")] <- ""


meth[c(
  "optimism_bias",
  "self_efficacy",
  "risk_perception",
  "locus_of_control",
  "acceptance",
  "negative_emotions"
)] <- "pmm"

pred <- make.predictorMatrix(dat_imp)
pred[,] <- 1
diag(pred) <- 0


pred["n_clicked", ] <- 0




set.seed(123)
imp <- mice(
  dat_imp,
  m = 100,
  method = meth,
  predictorMatrix = pred,
  maxit = 30
  
)


zvars <- c("optimism_bias","self_efficacy","risk_perception",
           "locus_of_control","acceptance","negative_emotions","age_num",
           "years_org_num")

fit_imp_z <- with(
  imp,
  {
    d <- data.frame(n_clicked, optimism_bias, self_efficacy, risk_perception,
                    locus_of_control, acceptance, negative_emotions,
                    age_num, gender_bin, JobRole_bin, years_org_num)

    for (v in intersect(zvars, names(d))) {
      d[[v]] <- as.numeric(scale(d[[v]]))
    }

    glm(
      cbind(n_clicked, 4 - n_clicked) ~
        optimism_bias + self_efficacy + risk_perception +
        locus_of_control + acceptance + negative_emotions +
        age_num + gender_bin + JobRole_bin + years_org_num,
      family = binomial(),
      data = d
    )
  }
)

res_z <- pool(fit_imp_z)
summary(res_z)


sum_z <- summary(res_z)

sum_z$OR        <- exp(sum_z$estimate)
sum_z$OR_low95  <- exp(sum_z$estimate - 1.96 * sum_z$std.error)
sum_z$OR_high95 <- exp(sum_z$estimate + 1.96 * sum_z$std.error)

sum_z[, c("term","estimate","std.error","p.value","OR","OR_low95","OR_high95")]



## ============================================================
##  forest plot 
## ============================================================

df_plot_manual <- tibble::tribble(
  ~Predictor, ~beta, ~SE, ~OR, ~OR_low, ~OR_high,
  "Optimism bias",        0.49, 0.20, 1.64, 1.10, 2.43,
  "Self-efficacy",       -0.26, 0.25, 0.77, 0.47, 1.25,
  "Risk perception",     -0.17, 0.14, 0.85, 0.65, 1.10,
  "Locus of control",    -0.24, 0.17, 0.79, 0.57, 1.09,
  "Acceptance",           0.14, 0.14, 1.15, 0.87, 1.52,
  "Negative emotions",    0.01, 0.12, 1.01, 0.79, 1.28
) %>%
  mutate(
    sig = (OR_low > 1) | (OR_high < 1),
    Predictor = factor(Predictor, levels = Predictor[order(OR, decreasing = TRUE)]))



p <- ggplot(df_plot_manual, aes(x = OR, y = Predictor)) +
  geom_vline(xintercept = 1, linetype = "dashed",
             linewidth = 0.7, color = "grey40") +
  geom_errorbarh(
    aes(xmin = OR_low, xmax = OR_high),
    height = 0.20,
    linewidth = 0.8,
    color = "grey30"
  ) +
  geom_point(
    aes(fill = sig),
    shape = 21,
    size = 3.6,
    color = "black"
  ) +
  scale_fill_manual(
    values = c(`TRUE` = "black", `FALSE` = "white"),
    guide = "none"
  ) +
  scale_x_log10(
    breaks = c(0.5, 0.75, 1, 1.25, 1.5, 2, 3),
    labels = c("0.5","0.75","1","1.25","1.5","2","3")
  ) +
  scale_y_discrete(limits = rev) +   
  labs(
    x = "Odds ratio (log scale) with 95% CI",
    y = NULL
  ) +
  theme_classic(base_size = 14) +
  theme(
    axis.text.y  = element_text(size = 15),
    axis.text.x  = element_text(size = 13),
    axis.title.x = element_text(size = 14),
    axis.line.y  = element_blank(),
    axis.ticks.y = element_blank(),
    plot.margin  = margin(10, 15, 10, 10)
  )

print(p)


ggsave(
  "forest_plot_odds_ratios.pdf",
  plot   = p,
  width  = 7,
  height = 4.5,
  units  = "in",
  device = cairo_pdf
)

##----------------------
##Histogram click sums and compromise probability
##----------------------

local({

  library(dplyr)
  library(tidyr)
  library(ggplot2)

 

  to_binary_present <- function(x) {
    x <- trimws(as.character(x))
    dplyr::case_when(
      is.na(x) | x == "" ~ 0L,
      x == "--"          ~ 0L,
      TRUE               ~ 1L
    )
  }

 
  to_clicked <- function(x) {
    x <- trimws(as.character(x))
    dplyr::case_when(
      is.na(x) | x == "" ~ 0L,
      x == "--"          ~ 0L,
      TRUE               ~ 1L
    )
  }

  
  wilson_ci <- function(x, n, z = 1.96) {
    if (n == 0) return(c(NA_real_, NA_real_))
    p <- x / n
    denom <- 1 + z^2 / n
    center <- (p + z^2/(2*n)) / denom
    half <- (z * sqrt((p*(1-p) + z^2/(4*n)) / n)) / denom
    c(center - half, center + half)
  }

  ## ----------------------------
  ## 1) Build per-person variables
  ## ----------------------------

  dat0 <- df_analysis_filt %>%
    mutate(
      
      sent_sim0  = to_binary_present(`sim0_Opened_Time_c1_2023-03-29`),
      sent_sim05 = to_binary_present(`sim0.5_Opened_Time_c2_2024-07-22`),
      sent_sim1  = to_binary_present(sim1_SuccessfullyDeliveredEmail_TimeStamp),
      sent_sim2  = to_binary_present(sim2_SuccessfullyDeliveredEmail_TimeStamp),

      
      clicked_sim0  = to_clicked(`sim0_Viewed Landing Page_Time_c1_2023-03-29`),
      clicked_sim05 = to_clicked(`sim0.5_Viewed Landing Page_Time_c2_2024-07-22`),
      clicked_sim1  = to_clicked(sim1_EmailLinkClicked_TimeStamp),
      clicked_sim2  = to_clicked(sim2_EmailLinkClicked_TimeStamp),

      
      clicked_sim0  = clicked_sim0  * sent_sim0,
      clicked_sim05 = clicked_sim05 * sent_sim05,
      clicked_sim1  = clicked_sim1  * sent_sim1,
      clicked_sim2  = clicked_sim2  * sent_sim2,

     
      compromised_sim0  = to_binary_present(`sim0_Data Entered_Time_c1_2023-03-29`),
      compromised_sim05 = to_binary_present(`sim0.5_Data Entered_Time_c2_2024-07-22`),
      compromised_sim1  = to_binary_present(sim1_CredSupplied_TimeStamp_Compromised),
      compromised_sim2  = to_binary_present(sim2_CredSupplied_TimeStamp_Compromised),

      
      compromised_sim0  = compromised_sim0  * sent_sim0,
      compromised_sim05 = compromised_sim05 * sent_sim05,
      compromised_sim1  = compromised_sim1  * sent_sim1,
      compromised_sim2  = compromised_sim2  * sent_sim2
    ) %>%
    mutate(
      n_sent = sent_sim0 + sent_sim05 + sent_sim1 + sent_sim2,
      n_clicked = clicked_sim0 + clicked_sim05 + clicked_sim1 + clicked_sim2,
      n_compromised = compromised_sim0 + compromised_sim05 + compromised_sim1 + compromised_sim2,
      any_compromise = if_else(n_compromised >= 1, "Compromised (>=1)", "Not compromised")
    )

  
  df_cc4 <- dat0 %>%
    filter(sent_sim0 == 1, sent_sim05 == 1, sent_sim1 == 1, sent_sim2 == 1) %>%
    mutate(n_sent = 4L)

  cat("N complete exposure (4/4):", nrow(df_cc4), "\n")

library(dplyr)
library(ggplot2)


wilson_ci <- function(x, n, z = 1.96) {
  if (is.na(n) || n == 0) return(c(NA_real_, NA_real_))
  p <- x / n
  denom <- 1 + z^2 / n
  center <- (p + z^2/(2*n)) / denom
  half <- (z * sqrt((p*(1-p) + z^2/(4*n)) / n)) / denom
  c(center - half, center + half)
}

sumdat <- df_cc4 %>%
  filter(n_clicked >= 1) %>%             
  group_by(n_clicked) %>%
  summarise(
    n_people = n(),
    clicks_total = sum(n_clicked, na.rm = TRUE),
    comp_total   = sum(n_compromised, na.rm = TRUE),
    rate_comp_per_click = comp_total / clicks_total,
    ci_low  = wilson_ci(comp_total, clicks_total)[1],
    ci_high = wilson_ci(comp_total, clicks_total)[2],
    .groups = "drop"
  )


k <- max(sumdat$n_people)

p <- ggplot(sumdat, aes(x = factor(n_clicked))) +
  
  geom_col(aes(y = n_people), fill = "grey40", color = "white") +

  
  geom_line(aes(y = rate_comp_per_click * k, group = 1), linewidth = 0.8) +
  geom_point(aes(y = rate_comp_per_click * k), size = 3) +

 
  geom_errorbar(
    aes(ymin = ci_low * k, ymax = ci_high * k),
    width = 0.10
  ) +

  scale_y_continuous(
    name = "Number of participants",
    sec.axis = sec_axis(~ . / k, name = "Compromise probability per click")
  ) +
  labs(x = "Number of phishing emails clicked (1–4)") +
  theme_classic(base_size = 16)

p

ggsave(
  "clickcount_with_compromise_per_click_overlay.pdf",
  plot = p, width = 6, height = 4, device = cairo_pdf
)

})

#####NEW

library(mice)
library(dplyr)

# ------------------------------------------------------------
# H3 donor-pool sensitivity analysis
# ------------------------------------------------------------

run_donor_sensitivity <- function(k) {

  # Nur die Anzahl der PMM-Donoren wird verändert
  imp_k <- mice(
    dat_imp,
    m = 100,
    method = meth,
    predictorMatrix = pred,
    maxit = 30,
    donors = k,
    seed = 123,
    printFlag = FALSE
  )

  # Identisches H3-Modell wie in der Hauptanalyse
  fit_k <- with(
    imp_k,
    {
      d <- data.frame(
        n_clicked,
        optimism_bias,
        self_efficacy,
        risk_perception,
        locus_of_control,
        acceptance,
        negative_emotions,
        age_num,
        gender_bin,
        JobRole_bin,
        years_org_num
      )

      # Identische Standardisierung wie in der Hauptanalyse
      for (v in intersect(zvars, names(d))) {
        d[[v]] <- as.numeric(scale(d[[v]]))
      }

      glm(
        cbind(n_clicked, 4 - n_clicked) ~
          optimism_bias +
          self_efficacy +
          risk_perception +
          locus_of_control +
          acceptance +
          negative_emotions +
          age_num +
          gender_bin +
          JobRole_bin +
          years_org_num,
        family = binomial(),
        data = d
      )
    }
  )

  # Pooling nach Rubin
  pooled_k <- summary(pool(fit_k))

  # Konfidenzintervalle und Odds Ratios
  pooled_k |>
    mutate(
      donors = k,
      critical_value = qt(.975, df),
      CI_low  = estimate - critical_value * std.error,
      CI_high = estimate + critical_value * std.error,
      OR = exp(estimate),
      OR_low95 = exp(CI_low),
      OR_high95 = exp(CI_high)
    )
}

# Donorpool-Größen vergleichen
donor_results <- bind_rows(
  lapply(c(1, 3, 5), run_donor_sensitivity)
)

# Ergebnisse für Optimism Bias
optimism_donor_results <- donor_results |>
  filter(term == "optimism_bias") |>
  select(
    donors,
    estimate,
    std.error,
    statistic,
    df,
    p.value,
    CI_low,
    CI_high,
    OR,
    OR_low95,
    OR_high95
  )

print(optimism_donor_results)

donor_results |>
  select(
    donors,
    term,
    estimate,
    std.error,
    p.value,
    CI_low,
    CI_high
  ) |>
  arrange(term, donors) |>
  tibble::as_tibble() |>
  print(n = Inf)

```




#Post Hoc Analysis Repeat Clicker (Hierarchical Modelling)
```{r}
## ============================================================
## H4: Repeat-clicker GLMM (4 time points)
## - Outcomes (clicked_*) NOT imputed
## - Predictors only imputed
## ============================================================

local({

  View <- function(...) invisible(NULL)

  library(dplyr)
  library(tidyr)
  library(lme4)
  library(mice)
  library(performance)

  set.seed(123)


  to_delivered <- function(x) {
    x <- trimws(as.character(x))
    dplyr::case_when(
      is.na(x) | x == "" ~ 0L,
      x == "--"          ~ 0L,
      TRUE               ~ 1L
    )
  }

  to_clicked <- function(x) {
    x <- trimws(as.character(x))
    dplyr::case_when(
      is.na(x) | x == "" ~ 0L,
      x == "--"          ~ 0L,
      TRUE               ~ 1L
    )
  }

  z <- function(x) as.numeric(scale(x))


  dat0 <- df_analysis_filt


  dat0 <- dat0 %>%
    mutate(
     
      sent_sim0  = to_delivered(`sim0_Opened_Time_c1_2023-03-29`),
      sent_sim05 = to_delivered(`sim0.5_Opened_Time_c2_2024-07-22`),
      sent_sim1 = to_delivered(sim1_SuccessfullyDeliveredEmail_TimeStamp),
      sent_sim2 = to_delivered(sim2_SuccessfullyDeliveredEmail_TimeStamp),


      
      clicked_sim0  = to_clicked(`sim0_Viewed Landing Page_Time_c1_2023-03-29`),
      clicked_sim05 = to_clicked(`sim0.5_Viewed Landing Page_Time_c2_2024-07-22`),
      clicked_sim1  = to_clicked(sim1_EmailLinkClicked_TimeStamp),
      clicked_sim2  = to_clicked(sim2_EmailLinkClicked_TimeStamp),

      
      clicked_sim0  = clicked_sim0  * sent_sim0,
      clicked_sim05 = clicked_sim05 * sent_sim05
    )


  dat_h4 <- dat0 %>%
    filter(sent_sim0 == 1, sent_sim05 == 1, sent_sim1 == 1, sent_sim2 == 1)

  cat("H4 base (same delivery filter as main pipeline) | N =", nrow(dat_h4), "\n")


  want <- c(
    "clicked_sim0","clicked_sim05","clicked_sim1","clicked_sim2",
    "optimism_bias","risk_perception","negative_emotions","acceptance",
    "self_efficacy","locus_of_control","feeling_attacked","per_orga_security",
    "age_num","gender_bin","JobRole_bin","years_org_num","anonymisedEmail"
  )
  dat_h4 <- dat_h4[, intersect(want, names(dat_h4)), drop = FALSE]


  if ("JobRole_bin" %in% names(dat_h4)) dat_h4$JobRole_bin <- factor(dat_h4$JobRole_bin)

  if ("gender_bin" %in% names(dat_h4)) {
    
    x <- suppressWarnings(as.integer(as.character(dat_h4$gender_bin)))
    x[!x %in% c(0L, 1L)] <- NA_integer_
    dat_h4$gender_bin <- factor(x, levels = c(0, 1))
  }


  click_vars <- intersect(c("clicked_sim0","clicked_sim05","clicked_sim1","clicked_sim2"), names(dat_h4))

  dat_h4[click_vars] <- lapply(dat_h4[click_vars], function(x) {
    x <- suppressWarnings(as.integer(as.character(x)))
    x[!x %in% c(0L, 1L)] <- NA_integer_
    x
  })

  cat("Unique IDs:", dplyr::n_distinct(dat_h4$anonymisedEmail), "\n")

  dat_h4 <- dat_h4 %>% filter(if_all(all_of(click_vars), ~ !is.na(.x)))
  cat("H4 complete outcomes (all 4 cycles observed) | N =", nrow(dat_h4), "\n")


  meth <- make.method(dat_h4)
  pred <- make.predictorMatrix(dat_h4)


  if ("anonymisedEmail" %in% names(dat_h4)) {
    meth["anonymisedEmail"] <- ""
    pred[, "anonymisedEmail"] <- 0
    pred["anonymisedEmail", ] <- 0
  }


  meth[click_vars] <- ""
  pred[, click_vars] <- 0


  for (v in intersect(c("age_num","gender_bin","JobRole_bin","years_org_num"), names(dat_h4))) {
    meth[v] <- ""
  }


  for (v in intersect(c("optimism_bias","risk_perception","negative_emotions",
                        "acceptance","self_efficacy","locus_of_control",
                        "feeling_attacked","per_orga_security"), names(dat_h4))) {
    meth[v] <- "pmm"
  }

  stopifnot(identical(names(meth), colnames(dat_h4)))

  imp <- mice(
    dat_h4,
    m = 30,
    method = meth,
    predictorMatrix = pred,
    maxit = 30,
    seed = 123
  )
  cat("Imputation finished (predictors only).\n")


  fits <- vector("list", imp$m)
  
  icc_vals <- numeric(imp$m)


  for (i in 1:imp$m) {

    d <- complete(imp, i)
    d$id <- factor(d$anonymisedEmail)

    if ("JobRole_bin" %in% names(d)) d$JobRole_bin <- factor(d$JobRole_bin)


    for (v in c("optimism_bias","risk_perception","negative_emotions","acceptance",
                "self_efficacy","locus_of_control","age_num","years_org_num",
                "feeling_attacked","per_orga_security")) {
      if (v %in% names(d) && is.numeric(d[[v]])) d[[v]] <- z(d[[v]])
    }

    long_i <- d %>%
      pivot_longer(
        cols = all_of(click_vars),
        names_to = "cycle",
        values_to = "clicked_bin"
      ) %>%
      mutate(
        cycle = factor(
          cycle,
          levels = c("clicked_sim0","clicked_sim05","clicked_sim1","clicked_sim2"),
          labels = c("sim0","sim0.5","sim1","sim2")
        ),
        clicked_bin = as.integer(clicked_bin),
        difficulty = case_when(
          cycle == "sim0"   ~ 1L,
          cycle == "sim0.5" ~ 2L,
          cycle == "sim1"   ~ 2L,
          cycle == "sim2"   ~ 3L
        )
      )

    rhs <- c(
      "difficulty",
      intersect(
        c("optimism_bias","risk_perception","negative_emotions","acceptance",
          "self_efficacy","locus_of_control","feeling_attacked","per_orga_security",
          "age_num","gender_bin","JobRole_bin","years_org_num"),
        names(long_i)
      )
    )

    form <- as.formula(paste("clicked_bin ~", paste(rhs, collapse = " + "), "+ (1 | id)"))

    fits[[i]] <- glmer(
      form,
      data = long_i,
      family = binomial("logit"),
      control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
    )

    icc_vals[i] <- performance::icc(fits[[i]])$ICC_adjusted

    
    r2_vals <- performance::r2_nakagawa(fits[[i]])
    cat(sprintf("Imputation %d: R2_marg = %.3f, R2_cond = %.3f\n",
                i, r2_vals$R2_marginal, r2_vals$R2_conditional))
  }


  betas <- lapply(fits, fixef)
  Vlist <- lapply(fits, vcov)
  m <- length(betas)

  coef_names <- names(betas[[1]])
  Q <- sapply(betas, function(b) setNames(b[coef_names], coef_names))

  qbar <- rowMeans(Q)
  Ubar <- Reduce("+", Vlist) / m
  Q_centered <- sweep(Q, 1, qbar, "-")
  B <- (Q_centered %*% t(Q_centered)) / (m - 1)
  Tmat <- Ubar + (1 + 1/m) * B

  se <- sqrt(diag(Tmat))
  zval <- qbar / se
  p <- 2 * pnorm(-abs(zval))

  out <- data.frame(
    term      = coef_names,
    estimate  = qbar,
    se        = se,
    z         = zval,
    p         = p,
    OR        = exp(qbar),
    OR_low95  = exp(qbar - 1.96 * se),
    OR_high95 = exp(qbar + 1.96 * se),
    stringsAsFactors = FALSE
  ) %>%
    mutate(
      p_fmt = format.pval(p, digits = 3, eps = 1e-3),
      OR_ci = sprintf("%.2f [%.2f, %.2f]", OR, OR_low95, OR_high95)
    ) %>%
    dplyr::select(term, estimate, se, z, p = p_fmt, OR_ci)

  cat("\n--- H4 pooled fixed effects (Rubin's rules; outcomes not imputed) ---\n")
  print(out, digits = 3)


  assign("dat_h4", dat_h4, envir = .GlobalEnv)


assign("icc_vals", icc_vals, envir = .GlobalEnv)
assign("fits", fits, envir = .GlobalEnv)


  
})

mean(icc_vals)
sd(icc_vals)
range(icc_vals)


```




#Qualitative data analysis
```{r}
library(ggplot2)


library(dplyr)

df_analysis_filt %>%
  count(reasons_click, sort = TRUE)





###

library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(tibble)

## -------------------
## 1) Closed-format options
## -------------------
## Derived from the multi-select `reasons_click` item on the analysis sample,
## rather than typed in. Each respondent may select several options, so these are
## counts of respondents choosing each option, not a partition of the 67 who
## answered. No further filter applies.
reasons_sel <- df_analysis_filt$reasons_click
reasons_sel <- reasons_sel[!is.na(reasons_sel) & reasons_sel != ""]
n_reason <- function(option) sum(grepl(option, reasons_sel, fixed = TRUE))

df_predef_raw <- tribble(
  ~raw, ~n,
  "legitimate",                                                   n_reason("thought that the e-mail was legitimate"),
  "Other reason:",                                                n_reason("Other reason:"),
  "I clicked on the link to find out if the e-mail was phishing", n_reason("to find out if the e-mail was phishing"),
  "Our security system would protect me from any harm",           n_reason("security system would protect me from any harm"),
  "I did not read the e-mail content and just clicked the link",  n_reason("did not read the e-mail content and just clicked the link")
)

cat("Closed-format reasons, respondents =", length(reasons_sel), "\n")
print(df_predef_raw)

## Fail the run rather than silently drifting from the published figure.
stopifnot(
  length(reasons_sel) == 67,
  df_predef_raw$n[df_predef_raw$raw == "legitimate"] == 40,
  df_predef_raw$n[df_predef_raw$raw == "I clicked on the link to find out if the e-mail was phishing"] == 4,
  df_predef_raw$n[df_predef_raw$raw == "Our security system would protect me from any harm"] == 6,
  df_predef_raw$n[df_predef_raw$raw == "I did not read the e-mail content and just clicked the link"] == 3
)

df_predef <- df_predef_raw %>%
  mutate(raw = as.character(raw)) %>%
  mutate(
    reason = str_squish(raw),
    reason = str_replace_all(reason, "\\s*:\\s*$", ""),
    reason = case_when(
      tolower(reason) == "legitimate" ~ "Thought email was legitimate",
      TRUE ~ reason
    )
  ) %>%
  group_by(reason) %>%
  summarise(n = sum(n), .groups = "drop") %>%
  filter(tolower(reason) != "other reason") %>%
  mutate(group = "Closed-format options")

## -------------------
## 2) Open-text (Other reasons)
## -------------------
df_other_codes <- tibble(
  reason = c(
    "Situational fit",
    "Distracted / stressed / multitasking",
    "On mobile device",
    "Seemed legitimate / curiosity",
    "Did not expect phishing",
    "Did not know how to differentiate",
    "Not marked as external"
  ),
  n = c(13, 12, 3, 2, 2, 1, 1),
  group = "Open-text (Other reasons)"
)

## -------------------
## 3) Combine + order within facets
## -------------------
df_all <- bind_rows(df_predef, df_other_codes) %>%
  mutate(
    group = factor(group, levels = c("Closed-format options", "Open-text (Other reasons)"))
  ) %>%
  arrange(group, desc(n)) %>%
  group_by(group) %>%
  mutate(reason = factor(reason, levels = rev(unique(reason)))) %>%  # order within each facet
  ungroup()

## -------------------
## 4) Plot (horizontal facet headers)
## -------------------
p_list <- ggplot(df_all, aes(x = reason, y = n)) +
  geom_col(fill = "grey30", width = 0.75) +
  coord_flip(clip = "off") +
  facet_wrap(~ group, ncol = 1, scales = "free_y") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  labs(x = NULL, y = "Number of participants") +
  theme_classic(base_size = 13) +
  theme(
    strip.text = element_text(size = 11, face = "bold"),
    strip.background = element_blank(),
    axis.text.y = element_text(size = 11),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 20)
  )

print(p_list)

ggsave(
  "self_reported_reasons_clicking_faceted.pdf",
  plot = p_list,
  width = 6.2,
  height = 4.8,
  units = "in",
  device = cairo_pdf
)
 

```



#Individual differences (exploratory analysis)

```{r}
df_mod <- df_analysis_filt |>
  mutate(
    optimism_c = optimism_bias - mean(optimism_bias, na.rm = TRUE)
  )

mod_a <- lm(
  negative_emotions ~ level_compromised_sim1 * optimism_c +
    age_num + gender_bin + jobrole_bin01 + years_org_num,
  data = df_mod
)
summary(mod_a)$coefficients["level_compromised_sim1:optimism_c", ]
```


#Psychological variables as a baseline for H4
```{r}
library(dplyr)
library(mice)
library(tibble)

# ------------------------------------------------------------
# Psychologische Prädiktoren
# ------------------------------------------------------------

psych_vars <- c(
  "optimism_bias",
  "self_efficacy",
  "risk_perception",
  "locus_of_control",
  "acceptance",
  "negative_emotions"
)

# ------------------------------------------------------------
# Analysedatensatz
#
# level_compromised_sim1 = Simulation 3
# level_compromised_sim2 = Simulation 4
# ------------------------------------------------------------

dat_t4_adjusted <- df_analysis_filt |>
  select(
    level_compromised_sim2,  # Outcome: Simulation 4
    level_compromised_sim1,  # vorheriger Compromise-Level
    all_of(psych_vars),
    age_num,
    gender_bin,
    jobrole_bin01,
    years_org_num
  )

# Outcomes sollten vollständig beobachtet sein
cat(
  "Missing Simulation 4 outcome values:",
  sum(is.na(dat_t4_adjusted$level_compromised_sim2)),
  "\n"
)

cat(
  "Missing Simulation 3 compromise values:",
  sum(is.na(dat_t4_adjusted$level_compromised_sim1)),
  "\n"
)

# ------------------------------------------------------------
# Imputationsmethoden
# Nur psychologische Prädiktoren werden imputiert
# ------------------------------------------------------------

meth_t4_adjusted <- make.method(dat_t4_adjusted)
meth_t4_adjusted[] <- ""
meth_t4_adjusted[psych_vars] <- "pmm"

# ------------------------------------------------------------
# Predictor Matrix
#
# Beide Compromise-Level und die Kontrollen dürfen die
# psychologischen Variablen vorhersagen, werden aber nicht
# selbst imputiert.
# ------------------------------------------------------------

pred_t4_adjusted <- make.predictorMatrix(dat_t4_adjusted)
pred_t4_adjusted[,] <- 0
pred_t4_adjusted[psych_vars, ] <- 1
diag(pred_t4_adjusted) <- 0

# ------------------------------------------------------------
# Multiple Imputation
# ------------------------------------------------------------

imp_t4_adjusted <- mice(
  dat_t4_adjusted,
  m = 100,
  maxit = 30,
  method = meth_t4_adjusted,
  predictorMatrix = pred_t4_adjusted,
  donors = 5,
  seed = 123,
  printFlag = FALSE
)

# Prüfen, ob mice Probleme dokumentiert hat
imp_t4_adjusted$loggedEvents

# ------------------------------------------------------------
# Multiple Regression
#
# AV: Compromise-Level in Simulation 4
# UVs: sechs psychologische Faktoren
# Kontrolle:
#   - Compromise-Level in Simulation 3
#   - Alter
#   - Geschlecht
#   - Job Role
#   - Job Tenure
# ------------------------------------------------------------

fit_t4_adjusted <- with(
  imp_t4_adjusted,
  lm(
    scale(level_compromised_sim2) ~
      scale(level_compromised_sim1) +
      scale(optimism_bias) +
      scale(self_efficacy) +
      scale(risk_perception) +
      scale(locus_of_control) +
      scale(acceptance) +
      scale(negative_emotions) +
      scale(age_num) +
      gender_bin +
      jobrole_bin01 +
      scale(years_org_num)
  )
)

# ------------------------------------------------------------
# Rubin-Pooling
# ------------------------------------------------------------

pooled_t4_adjusted <- pool(fit_t4_adjusted)
t4_adjusted_results <- summary(pooled_t4_adjusted)

# Konfidenzintervalle
t4_adjusted_results <- t4_adjusted_results |>
  mutate(
    critical_value = qt(.975, df),
    CI_low  = estimate - critical_value * std.error,
    CI_high = estimate + critical_value * std.error
  )

# ------------------------------------------------------------
# Ergebnisse der sechs psychologischen Prädiktoren
# ------------------------------------------------------------

psych_results_t4_adjusted <- t4_adjusted_results |>
  filter(grepl(
    paste(psych_vars, collapse = "|"),
    term
  )) |>
  select(
    term,
    estimate,
    std.error,
    statistic,
    df,
    p.value,
    CI_low,
    CI_high
  ) |>
  as_tibble()

print(psych_results_t4_adjusted, n = Inf)

# ------------------------------------------------------------
# Vollständige Tabelle einschließlich vorherigem Compromise
# und demografischen Kontrollen
# ------------------------------------------------------------

t4_adjusted_results |>
  select(
    term,
    estimate,
    std.error,
    statistic,
    df,
    p.value,
    CI_low,
    CI_high
  ) |>
  as_tibble() |>
  print(n = Inf)

```


